---
title: "8_ZonalHist_MultScens_50Years_graphs"
author: "Sarah Halperin"
date: "August 7, 2018"
output:
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

## Introduction 

Purpose: Combined merged zonal tables and use them to make ggplots. 
Creator: Sarah Halperin 
Contact: halperins@si.edu 

Input: U:\CLI\Dinamica_Runs\StudyArea_V201\SA_V2016\BasicDataAnalyses\Zonal_Histogram 

Output: U:\CLI\Dinamica_Runs\StudyArea_V201\SA_V2016\BasicDataAnalyses\OutputVisuals\ZonalHistogram_ggplots 
  
  Note: Outputs may also be in certain presentation folders 

### Packages Needed 

```{r error=FALSE, message=FALSE, warning=FALSE}
library(plyr) # General data manipulation
library(dplyr) # General data manipulation
library(raster) # read and edit rasters
library(rgdal)
library(reshape) #manipulation of output tables 
library(ggplot2) #graphs 
library(ggpubr)
library(ggrepel) #changes to graphs
```

### Input Files 
```{r, eval=FALSE}
version<-"/StudyArea_V201/SA_V2015"
version_table<-paste0("U:/CLI/Dinamica_Runs",version, "/BasicDataAnalyses/Zonal_Histogram/")
tables<-"Tables/v2016_"
```

ALL Scenario Tables. If not created use Rscript 8_ZonalHist_50years_MergeTables

###Output Files
```{r, eval=FALSE}
Comb_outputCounty<-paste0(version_table, tables, "County/")
Comb_outputSA<-paste0(version_table, tables,"StudyArea/")
Comb_outputBuffer<-paste0(version_table,tables, "Buffer/")
Comb_outputRegion<-paste0(version_table, tables, "Region/")
Comb_outputReshape<-paste0(version_table, tables, "County/v2016_Reshape/")
```

##CODE BEGINS

###County Tables 
```{r, eval=FALSE}
FolderM<-list.files(Comb_outputCounty, pattern="ctny.csv", full.names = TRUE) 
CSV_Melt<-lapply(FolderM,function(i){
  read.csv(i)
})


#ADD SCENARIO 
CSV_Melt[[1]]$Scenario<-"Q1"
CSV_Melt[[2]]$Scenario<-"Q2"
CSV_Melt[[3]]$Scenario<-"Q3"
CSV_Melt[[4]]$Scenario<-"Q4"
CSV_Melt[[5]]$Scenario<-"RT"

CombinedMeltLC<-do.call(rbind.data.frame,CSV_Melt)
CombinedMeltLC<-subset(CombinedMeltLC, CombinedMeltLC$TimeStep > 1) #IF STILL NEED AFTER 2001
write.csv(CombinedMeltLC, paste0(Comb_outputCounty,"v2016_ZonalHistogram_AllScenarios_ctny", ".csv"), row.names=FALSE)
```

###Counties within study area
```{r , eval=FALSE}
FolderM_SA<-list.files(Comb_outputCounty, pattern="SA.csv", full.names = TRUE) 
CSV_Melt_SA<-lapply(FolderM_SA,function(i){
  read.csv(i)
})


#ADD SCENARIO 
CSV_Melt_SA[[1]]$Scenario<-"Q1"
CSV_Melt_SA[[2]]$Scenario<-"Q2"
CSV_Melt_SA[[3]]$Scenario<-"Q3"
CSV_Melt_SA[[4]]$Scenario<-"Q4"
CSV_Melt_SA[[5]]$Scenario<-"RT"

CombinedMeltLC_SA<-do.call(rbind.data.frame,CSV_Melt_SA)
CombinedMeltLC_SA<-subset(CombinedMeltLC_SA, CombinedMeltLC_SA$TimeStep > 1) #IF STILL NEED AFTER 2001
write.csv(CombinedMeltLC_SA, paste0(Comb_outputCounty,"v2016_ZonalHistogram_AllScenarios_ctny_SA", ".csv"), row.names=FALSE)
```

###Region 
```{r, eval=FALSE}
FolderMR<-list.files(Comb_outputRegion, pattern="rgn.csv", full.names = TRUE) 
CSV_Region<-lapply(FolderMR,function(i){
  read.csv(i)
})


#ADD SCENARIO 
CSV_Region[[1]]$Scenario<-"Q1"
CSV_Region[[2]]$Scenario<-"Q2"
CSV_Region[[3]]$Scenario<-"Q3"
CSV_Region[[4]]$Scenario<-"Q4"
CSV_Region[[5]]$Scenario<-"RT"

CombinedRegionLC<-do.call(rbind.data.frame,CSV_Region)
CombinedRegionLC<-subset(CombinedRegionLC, CombinedRegionLC$TimeStep > 1)
write.csv(CombinedRegionLC, paste0(Comb_outputRegion,"v2016_ZonalHistogram_AllScenarios_rgn", ".csv"), row.names=FALSE)
```
###Region study area 
```{r, eval=FALSE}
FolderMR_SA<-list.files(Comb_outputRegion, pattern="SA.csv", full.names = TRUE) 
CSV_Region_SA<-lapply(FolderMR_SA,function(i){
  read.csv(i)
})


#ADD SCENARIO 
CSV_Region_SA[[1]]$Scenario<-"Q1"
CSV_Region_SA[[2]]$Scenario<-"Q2"
CSV_Region_SA[[3]]$Scenario<-"Q3"
CSV_Region_SA[[4]]$Scenario<-"Q4"
CSV_Region_SA[[5]]$Scenario<-"RT"

CombinedRegionLC_SA<-do.call(rbind.data.frame,CSV_Region_SA)
CombinedRegionLC_SA<-subset(CombinedRegionLC_SA, CombinedRegionLC_SA$TimeStep > 1) #IF STILL NEED AFTER 2001
write.csv(CombinedRegionLC_SA, paste0(Comb_outputRegion,"V21016_ZonalHistogram_AllScenarios_rgn_SA", ".csv"), row.names=FALSE)
```
###Aggregated tables full study area 
```{r, eval=FALSE}
FolderS<-list.files(Comb_outputBuffer, pattern=".csv", full.names = TRUE) 
CSV_Sum<-lapply(FolderS,function(i){
  read.csv(i)
})


CSV_Sum[[1]]$Scenario<-"Q1"
CSV_Sum[[2]]$Scenario<-"Q2"
CSV_Sum[[3]]$Scenario<-"Q3"
CSV_Sum[[4]]$Scenario<-"Q4"
CSV_Sum[[5]]$Scenario<-"RT"

CombinedSumLC<-do.call(rbind.data.frame,CSV_Sum)
write.csv(CombinedSumLC, paste0(Comb_outputBuffer,"v2016_ZonalHistogram_AllScenarios_Buffer.csv"), row.names=FALSE)
```
###Aggregated tables study area only 
```{r, eval=FALSE}
FolderS_SA<-list.files(Comb_outputSA, pattern=".csv", full.names = TRUE) 
CSV_Sum_SA<-lapply(FolderS_SA,function(i){
  read.csv(i)
})



CSV_Sum_SA[[1]]$Scenario<-"Q1"
CSV_Sum_SA[[2]]$Scenario<-"Q2"
CSV_Sum_SA[[3]]$Scenario<-"Q3"
CSV_Sum_SA[[4]]$Scenario<-"Q4"
CSV_Sum_SA[[5]]$Scenario<-"RT"

CombinedSumLC_SA<-do.call(rbind.data.frame,CSV_Sum_SA)
write.csv(CombinedSumLC_SA, paste0(Comb_outputSA,"v2016_ZonalHistogram_AllScenarios_SA.csv"), row.names=FALSE)
```

##IMPORTANT: IF THESE TABLES ARE ALREADY MADE YOU CAN PULL IN THE FILES DIRECTLY

For example 

```{r}
CombinedMeltPC<-read.csv("U:/CLI/Dinamica_Runs/StudyArea_V201/SA_V2016/BasicDataAnalyses/Zonal_Histogram/Tables/v2016_County/v2016_ZonalHistogram_AllScenarios_ctny_SA.csv")
```

```{r, eval=FALSE}
CombinedSumPC<-read.csv("U:/CLI/Dinamica_Runs/StudyArea_V201/SA_V2016/BasicDataAnalyses/Zonal_Histogram/Tables/v2016_StudyArea/v2016_ZonalHistogram_AllScenarios_SA.csv")
```

##GRAPHS 
###COUNTY GRAPHS SET UP 

Code to get a percent change for individual counties. We have not been using this anymore. MAY HAVE TO CHANGE WHAT THE ORIGINAL SUBSET IS BASED ON WHICH FILES YOU BROGHT IN ABOVE.

```{r, eval=FALSE}
CombinedMeltLC<-CombinedSumLC_SA #set combinedmeltlc_sa to combinedmeltlc if want just study area 
#CombinedMeltLC<-CombinedSumLC 

CombinedMeltLC$Rowid_<-NULL

CombinedMeltLCT2<-subset(CombinedMeltLC, CombinedMeltLC$TimeStep ==2)
CombinedMeltLCT7<-subset(CombinedMeltLC, CombinedMeltLC$TimeStep ==7)
CombinedMeltLC27<-cbind(CombinedMeltLCT2,CombinedMeltLCT7)


CombinedMeltLC27<-CombinedMeltLC27[,c(1,2,3,4,6,7)]
CombinedMeltLC27<-mutate(CombinedMeltLC27, PercentChange=((valuekm.1-valuekm)/valuekm)*100)
CombinedMeltLC27$PercentChange<-round(CombinedMeltLC27$PercentChange, digits = 2)
#CombinedMeltLC27$PercentChange<-paste0(CombinedMeltLC27$PercentChange,"%")


CombinedMeltLC27$TimeStep<-7
PercentChangeMelt<-CombinedMeltLC27[,c(1,2,4,7)]

CombinedMeltPC<-merge(CombinedMeltLC,PercentChangeMelt, by=c("Scenario","TimeStep","LABEL"), all.x=TRUE)

CombinedMeltPC<-subset(CombinedMeltPC, TimeStep > 1)
```

SUBSET BY LANDCOVER TYPE 
```{r}
DevelopmentM<-subset(CombinedMeltPC, CombinedMeltPC$LABEL == "3")
ForestM<-subset(CombinedMeltPC, CombinedMeltPC$LABEL == "5")
GrassM<-subset(CombinedMeltPC, CombinedMeltPC$LABEL == "6")
CropM<-subset(CombinedMeltPC, CombinedMeltPC$LABEL == "7")
```

SUBSET BY COUNTY EXAMPLE 
```{r, eval=FALSE}
Loudoun<-subset(CombinedMeltPC, CombinedMeltPC$variable == "GEOID_51107")
Frederick<-subset(CombinedMeltPC, CombinedMeltPC$variable == "GEOID_51069")
Fauquier<-subset(CombinedMeltPC, CombinedMeltPC$variable == "GEOID_51061")
Shenandoah<-subset(CombinedMeltPC, CombinedMeltPC$variable == "GEOID_51171")
Albemarle<-subset(CombinedMeltPC, CombinedMeltPC$variable == "GEOID_51003")
Rockingham<-subset(CombinedMeltPC, CombinedMeltPC$variable == "GEOID_51165")
```

SUBSET BY COUNTY AND LANDCOVER TYPE EXAMPLE 
```{r}
FauquierD<-subset(DevelopmentM, DevelopmentM$variable == "GEOID_51061")
FauquierF<-subset(ForestM, ForestM$variable == "GEOID_51061")
FauquierG<-subset(GrassM, GrassM$variable == "GEOID_51061")
FauquierC<-subset(CropM, CropM$variable == "GEOID_51061")


FrederickD<-subset(DevelopmentM, DevelopmentM$variable == "GEOID_51069")
FrederickF<-subset(ForestM, ForestM$variable == "GEOID_51069")
FrederickG<-subset(GrassM, GrassM$variable == "GEOID_51069")
FrederickC<-subset(CropM, CropM$variable == "GEOID_51069")
```

###REGION GRAPHS SET UP

Percent Change Region 

```{r, eval=FALSE}
CombinedRegionLC<-CombinedRegionLC_SA #set study area equal if want graphs just for study area. Saves repeating a bunch of code.

CombinedRegionLC$Rowid_<-NULL

CombinedRegionLCT2<-subset(CombinedRegionLC, CombinedRegionLC$TimeStep ==2)
CombinedRegionLCT7<-subset(CombinedRegionLC, CombinedRegionLC$TimeStep ==7)
CombinedRegionLC27<-cbind(CombinedRegionLCT2,CombinedRegionLCT7)


CombinedRegionLC27<-CombinedRegionLC27[,c(1,2,3,5,6,7,8,13)]
CombinedRegionLC27<-mutate(CombinedRegionLC27, PercentChange=((valuekm.1-valuekm)/valuekm)*100)
CombinedRegionLC27$PercentChange<-round(CombinedRegionLC27$PercentChange, digits = 0)
CombinedRegionLC27$PercentChange<-paste0(CombinedRegionLC27$PercentChange,"%")


CombinedRegionLC27$TimeStep<-7
PercentChangeRegion<-CombinedRegionLC27[,c(1,2,3,7,9)]

CombinedRegionPC<-merge(CombinedRegionLC,PercentChangeRegion, by=c("Scenario","TimeStep","LABEL","variable"), all.x=TRUE)
```


###FULL STUDY AREA SET UP 

Percent change-- we don't really use anymore
```{r, eval=FALSE}
#CombinedSumLC<-CombinedSumLC_SA #set equal to study area if desired 
CombinedSumLC<-CombinedSumLC_SA

CombinedSumLCT2<-subset(CombinedSumLC, CombinedSumLC$TimeStep ==2)
CombinedSumLCT7<-subset(CombinedSumLC, CombinedSumLC$TimeStep ==7)
CombinedSumLC27<-cbind(CombinedSumLCT2,CombinedSumLCT7)
CombinedSumLC27<-CombinedSumLC27[,c(1,2,3,4,7,8)]
CombinedSumLC27<-mutate(CombinedSumLC27, PercentChange=((valuekm.1-valuekm)/valuekm)*100) #calculate percent change after only haveing time step 2 and 7
CombinedSumLC27$PercentChange<-round(CombinedSumLC27$PercentChange, digits = 2)


CombinedSumLC27$TimeStep<-7
PercentChange<-CombinedSumLC27[,c(1,2,4,7)]

CombinedSumPC<-merge(CombinedSumLC,PercentChange, by=c("Scenario","TimeStep","LABEL"), all.x=TRUE)
```

SUBSET BY LANDCOVER 
```{r, eval=FALSE}
DevelopmentPC<-subset(CombinedSumPC, CombinedSumPC$LABEL == "3")
ForestPC<-subset(CombinedSumPC, CombinedSumPC$LABEL == "5")
GrassPC<-subset(CombinedSumPC, CombinedSumPC$LABEL == "6")
CropPC<-subset(CombinedSumPC, CombinedSumPC$LABEL == "7")

#Remove Timestep 1
DevelopmentPC<-subset(DevelopmentPC, DevelopmentPC$TimeStep > 1)
ForestPC<-subset(ForestPC, ForestPC$TimeStep > 1)
GrassPC<-subset(GrassPC, GrassPC$TimeStep >1)
CropPC<-subset(CropPC, CropPC$TimeStep>1)
```


###GGPLOTS 

####Landcover type: compare scenarios (full study area)

```{r, fig.width=15, fig.height=15, eval=FALSE}
library(ggplot2) 

#NEED TO NAME TO HAVE IT SAVE AS A PNG


#Development 
ggplot(DevelopmentPC, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=2)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c( "2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
    #development#
  scale_y_continuous(name =expression('Total Area km'^2),  limits=c(575,1100), breaks=c(600,700,800,900,1000))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=40), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
#Forest
ggplot(ForestPC, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=2)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c( "2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
    #Forest#
  scale_y_continuous(name =expression('Total Area km'^2), limits = c(9550,9950), breaks=c(9600,9700,9800,9900))+
   theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=40), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
#GRASS 
ggplot(GrassPC, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=2)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c( "2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  #grass# 
  scale_y_continuous(name =expression('Total Area km'^2), limits=c(5250,5350), breaks=c(5275,5300,5325,5350))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=40), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
#Crop
ggplot(CropPC, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=2)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c( "2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  #crop#
  scale_y_continuous(name =expression('Total Area km'^2), limits=c(550,640), breaks=c(550,575,600,625))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=40), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

```{r, eval=FALSE}
setwd("U:/CLI/Dinamica_Runs/StudyArea_V201/SA_V2016/BasicDataAnalyses/OutputVisuals/ZonalHistogram_ggplots/v2016_StudyArea/")
png("v2016_SA_Grass.png", width=480, height=480, units="px", res=300) #can't put units and resolution
Grass
dev.off()


ggsave(file="v2016_SA_Grass.png", dpi=300,width=15, height=15)
```

####Individual counties 

Fauquier
```{r, fig.width=15, fig.height=15}
#Development 
ggplot(FauquierD, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=3)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c("2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  #development#
  scale_y_continuous(name =expression('Total Area km'^2),  limits=c(0,125), breaks=c(25,50,75,100,125))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+#+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
#Forest
ggplot(FauquierF, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=3)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c("2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  #Forest#
  scale_y_continuous(name =expression('Total Area km'^2), limits = c(675,775), breaks=c(675,700,725,750,775))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+#+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
#Grass 
ggplot(FauquierG, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=3)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c("2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
   #grass# 
  scale_y_continuous(name =expression('Total Area km'^2), limits=c(550,615), breaks=c(550,565,580,595,610))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+#+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

#Crop
ggplot(FauquierC, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=3)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c("2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
    #crop# 
  scale_y_continuous(name =expression('Total Area km'^2), limits=c(115,151), breaks=c(115,125,135,145))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+#+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

```{r, eval=FALSE}
setwd("U:/CLI/Presentations/ESA-08-XX-2018")
png("v2016_Fauq_Crop.png", width=480, height=480, units="px", res=300) #can't put units and resolution
FauqC
dev.off()


ggsave(file="v2016_Fauq_Crop.png", dpi=300,width=15, height=15)

```

Frederick 
```{r, fig.width=15, fig.height=15}
#Development
ggplot(FrederickD, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=3)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c("2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
    #development#
  scale_y_continuous(name =expression('Total Area km'^2), limits=c(50,150), breaks=c(50,75,100,125,150))+
    theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+#+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

#Forest 
ggplot(FrederickF, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=3)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c("2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  #Forest#
  scale_y_continuous(name =expression('Total Area km'^2), limits=c(525,625), breaks=c(525,550,575,600,625))+
    theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+#+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
#Grass
ggplot(FrederickG, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=3)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c("2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
    #grass#
  scale_y_continuous(name =expression('Total Area km'^2), limits=c(300,330), breaks=c(305,310,315,320,325))+
    theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+#+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
#Crop
ggplot(FrederickC, aes(x=TimeStep, y=valuekm, colour=Scenario, group=Scenario))+
  geom_line(size=3)+
  scale_x_continuous(name= "Time Step", breaks= c(2,3,4,5,6,7), labels=c("2011", "2021", "2031", "2041", "2051", "2061"))+
  scale_colour_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
    #crop#
  scale_y_continuous(name =expression('Total Area km'^2), limits=c(10,16), breaks=c(10,11,12,13,14,15))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+#+
  #geom_label_repel(aes(label=ifelse(is.na(PercentChange),"",paste0(PercentChange,"%"))), size=20, show.legend=FALSE)+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

```{r, eval=FALSE}
setwd("U:/CLI/Presentations/ESA-08-XX-2018")
png("v2016_Fred_Development.png", width=480, height=480, units="px", res=300) #can't put units and resolution
FredD
dev.off()


ggsave(file="v2016_Fred_Development.png", dpi=300,width=15, height=15)
```


