---
title: "8_ZonalHist_MultScens_50years"
author: "Sarah Halperin"
date: "August 6, 2018"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

## INTRODUCTION

Purpose: Combined and Hist for NLCD land cover years 2001 & 2011. Avoid using ArcMap and doing all steps by hand. 

Input: Regional layer and county table with "Din_cty" and "GEOID", initial landscape layer, final landscape layer. 

Output: Zonal histogram of transcrips between initial and final, zonal histogram of final landscape, raster of change in landscape. 

DEVELOPED: 
V1	2/18/2016 - Valentine Herrmann 
V2	5/2016 - Valentine Herrmann 
V3	6/1/2016 - Iara Lacher - Created raster with persistent land use in addition to changes in land use.
V4	3/30/2017 - Iara Lacher - Loop through recent trends and scenarios 50 years out
V5 4/3/2018 - Sarah Halperin - Options for each scenario over 5 timesteps 

CONTACT: LacherI@si.edu 

This script would be the equivalent of:
opening ArcMap, adding cblcd_92_an.img, cblcd_01_an.img and cblcd_1_an.img
   using "combine" on cblcd_92_an.img and cblcd_01_an.img, then on cblcd_01_an.img and  cblcd_11_an.img to create raster comb_9201 and comb_0111
using "zonal histogram " on comb_9201 and cblcd_01_an.img
using "zonal histogram " on comb_0111 and cblcd_11_an.img
merge zonal histogram into on table 
expoRT merged table to .txt files

3-2018 

Sarah Halperin: added code to loop through different scenarios 

IMPORTANT: USE eval= FALSE to turn off code you don't want to use 

## PACKAGES NEEDED 

```{r,warning=FALSE, message=FALSE}
library(plyr) # General data manipulation
library(dplyr) # General data manipulation
library(raster) # read and edit rasters
library(rgdal)
library(reshape) #manipulation of output tables 
library(ggplot2) #graphs 
library(ggpubr)
```

## INPUT FILES 
 

```{r message=FALSE, warning=FALSE}
version<-"/StudyArea_V201/SA_V2016"
version_input<-paste0("U:/CLI/Dinamica_Runs",version, "/FutureLandscapes/")
Scenario<-"RT/" #OPTIONS, RT, Q1, Q2,Q3,Q4,NL, PL_Gap, All
```

## FILE PATHS 

Set location for the input study area rasters 
```{r}
cntyRasterLoc <- "U:/CLI/PreparedRasters/StudyAreaBndy/" 
```

TURN ON SCENARIO INPUTS: what ever is turned on must match the designated scenario 

RUN FOR NL 
```{r, eval=FALSE }
inRasterLoc<-paste0(version_input, "NL/nlcd_nlcd/")
```


RUN FOR ALL INDIVIDUAL SCENARIOS
```{r}
inRasterLoc <- paste0(version_input, Scenario)
```


RUN FOR ALL SCENARIOS (not NL which needs to be run by itself)
```{r, eval=FALSE}
inRasterLoc<-version_input
Folders <-  list('Q1' = c("Q1/"),'Q1' = c("Q1/"),'Q1' = c("Q1/"),'Q1' = c("Q1/"),'Q1' = c("Q1/"),'Q2' = c("Q2/"),'Q2' = c("Q2/"),'Q2' = c("Q2/"),'Q2' = c("Q2/"),'Q2' = c("Q2/"),'Q3' = c("Q3/"),'Q3' = c("Q3/"),'Q3' = c("Q3/"),'Q3' = c("Q3/"),'Q3' = c("Q3/"),'Q4' = c("Q4/"),'Q4' = c("Q4/"),'Q4' = c("Q4/"),'Q4' = c("Q4/"),'Q4' = c("Q4/"),'RT' = c("RT/"),'RT' = c("RT/"),'RT' = c("RT/"),'RT' = c("RT/"),'RT' = c("RT/"))
inRasterLoc <-paste0(inRasterLoc, Folders)
```

RUN FOR PL_GAP
```{r, eval=FALSE}
inRasterLoc <- paste0(version_input, Scenario)
```


## COUNTY RASTER VALUES 
```{r}
counties <- raster(paste(cntyRasterLoc, "cnty_an", ".img", sep=""))
counties_vals <- getValues(counties)

sa_ctyGEOID<-read.csv("U:/CLI/Dinamica_Runs/StudyArea_V201/CountyNmsGEOID_cnty.csv")
colnames(sa_ctyGEOID)<-c("Din_cty", "GEOID","NAME")
sa_ctyGEOID$NAME<-NULL
str(sa_ctyGEOID)


#add leading zero to numbers with less than 1 digit
sa_ctyGEOIDzero<-sa_ctyGEOID
sa_ctyGEOIDzero$Din_cty<-sapply(sa_ctyGEOIDzero$Din_cty, function(x){if(nchar(x)<2){paste0(0,x)}else{x}}) #values 1-8 for the region. 


 #select only the Study Area counties to run basic analyses
S20_GEOID <-  read.csv("U:/CLI/Dinamica_Runs/StudyArea_V201/SAcntyOnly.csv")#SCBI V: #Geological ID for the county. 
```

## OUTPUT FOLDER 
```{r}
version_output<-"BasicDataAnalyses/Zonal_Histogram/"
Comb_output<-gsub("FutureLandscapes/", version_output, version_input)
Comb_output<-paste0(Comb_output, Scenario)
```


## CODE BEGINS 

```{r}
version_LS_trans<-"v2016" #must match above 
```

RUN FOR NL
```{r}
LS_trans <-  list('LS01' = c("nlcd01_anC.img"),'LS02' = c("nlcd11_anC.img"))
```

RUN FOR RT 
```{r}
LS_trans <-  list('LS01' = c(paste0(version_LS_trans,"_RT_Landscape01.tif")),'LS02' = c(paste0(version_LS_trans, "_RT_Landscape02.tif")),'LS03' = c(paste0(version_LS_trans,"_RT_Landscape03.tif")),'LS04' = c(paste0(version_LS_trans,"_RT_Landscape04.tif")),'LS05' = c(paste0(version_LS_trans,"_RT_Landscape05.tif"))) 
```
TURN ON FOR Q1 
```{r}
LS_trans <-  list('LS01' = c(paste0(version_LS_trans,"_Q1_Landscape01.tif")),'LS02' = c(paste0(version_LS_trans, "_Q1_Landscape02.tif")),'LS03' = c(paste0(version_LS_trans,"_Q1_Landscape03.tif")),'LS04' = c(paste0(version_LS_trans,"_Q1_Landscape04.tif")),'LS05' = c(paste0(version_LS_trans,"_Q1_Landscape05.tif")))
```

TURN ON FOR Q2
```{r}
LS_trans <-  list('LS01' = c(paste0(version_LS_trans,"_Q2_Landscape01.tif")),'LS02' = c(paste0(version_LS_trans, "_Q2_Landscape02.tif")),'LS03' = c(paste0(version_LS_trans,"_Q2_Landscape03.tif")),'LS04' = c(paste0(version_LS_trans,"_Q2_Landscape04.tif")),'LS05' = c(paste0(version_LS_trans,"_Q2_Landscape05.tif")))
```

TURN ON FOR Q3
```{r}
LS_trans <-  list('LS01' = c(paste0(version_LS_trans,"_Q3_Landscape01.tif")),'LS02' = c(paste0(version_LS_trans, "_Q3_Landscape02.tif")),'LS03' = c(paste0(version_LS_trans,"_Q3_Landscape03.tif")),'LS04' = c(paste0(version_LS_trans,"_Q3_Landscape04.tif")),'LS05' = c(paste0(version_LS_trans,"_Q3_Landscape05.tif")))
```

TURN ON FOR Q4
```{r}
LS_trans <-  list('LS01' = c(paste0(version_LS_trans,"_Q4_Landscape01.tif")),'LS02' = c(paste0(version_LS_trans, "_Q4_Landscape02.tif")),'LS03' = c(paste0(version_LS_trans,"_Q4_Landscape03.tif")),'LS04' = c(paste0(version_LS_trans,"_Q4_Landscape04.tif")),'LS05' = c(paste0(version_LS_trans,"_Q4_Landscape05.tif")))
```

TURN ON FOR ALL SCENARIOS 
```{r}
RT <-  list('LSRT01' = c(paste0(version_LS_trans,"_RT_Landscape01.tif")),'LSRT02' = c(paste0(version_LS_trans, "_RT_Landscape02.tif")),'LSRT03' = c(paste0(version_LS_trans,"_RT_Landscape03.tif")),'LSRT04' = c(paste0(version_LS_trans,"_RT_Landscape04.tif")),'LSRT05' = c(paste0(version_LS_trans,"_RT_Landscape05.tif"))) 

Q1 <-  list('LSQ101' = c(paste0(version_LS_trans,"_Q1_Landscape01.tif")),'LSQ102' = c(paste0(version_LS_trans, "_Q1_Landscape02.tif")),'LSQ103' = c(paste0(version_LS_trans,"_Q1_Landscape03.tif")),'LSQ104' = c(paste0(version_LS_trans,"_Q1_Landscape04.tif")),'LSQ105' = c(paste0(version_LS_trans,"_Q1_Landscape05.tif")))

Q2 <-  list('LSQ201' = c(paste0(version_LS_trans,"_Q2_Landscape01.tif")),'LSQ202' = c(paste0(version_LS_trans, "_Q2_Landscape02.tif")),'LSQ203' = c(paste0(version_LS_trans,"_Q2_Landscape03.tif")),'LSQ204' = c(paste0(version_LS_trans,"_Q2_Landscape04.tif")),'LSQ205' = c(paste0(version_LS_trans,"_Q2_Landscape05.tif")))


Q3<-  list('LSQ301' = c(paste0(version_LS_trans,"_Q3_Landscape01.tif")),'LSQ302' = c(paste0(version_LS_trans, "_Q3_Landscape02.tif")),'LSQ303' = c(paste0(version_LS_trans,"_Q3_Landscape03.tif")),'LSQ304' = c(paste0(version_LS_trans,"_Q3_Landscape04.tif")),'LSQ305' = c(paste0(version_LS_trans,"_Q3_Landscape05.tif")))


Q4 <-  list('LSQ401' = c(paste0(version_LS_trans,"_Q4_Landscape01.tif")),'LSQ402' = c(paste0(version_LS_trans, "_Q4_Landscape02.tif")),'LSQ403' = c(paste0(version_LS_trans,"_Q4_Landscape03.tif")),'LSQ404' = c(paste0(version_LS_trans,"_Q4_Landscape04.tif")),'LSQ405' = c(paste0(version_LS_trans,"_Q4_Landscape05.tif")))


LS_trans<-do.call(c,(list(Q1, Q2, Q3, Q4,RT)))
```

TURN ON FOR PL_GAP 
```{r}
NL<-list('LSNL01' = c("nldc01_anC.tif"),'LSNL02' = c("nldc11_anC.tif"))
RT <-  list('LSRT01' = c(paste0(version_LS_trans,"_RT_Landscape01.tif")),'LSRT02' = c(paste0(version_LS_trans, "_RT_Landscape02.tif")),'LSRT03' = c(paste0(version_LS_trans,"_RT_Landscape03.tif")),'LSRT04' = c(paste0(version_LS_trans,"_RT_Landscape04.tif")),'LSRT05' = c(paste0(version_LS_trans,"_RT_Landscape05.tif"))) 

Q1 <-  list('LSQ101' = c(paste0(version_LS_trans,"_Q1_Landscape01.tif")),'LSQ102' = c(paste0(version_LS_trans, "_Q1_Landscape02.tif")),'LSQ103' = c(paste0(version_LS_trans,"_Q1_Landscape03.tif")),'LSQ104' = c(paste0(version_LS_trans,"_Q1_Landscape04.tif")),'LSQ105' = c(paste0(version_LS_trans,"_Q1_Landscape05.tif")))

Q2 <-  list('LSQ201' = c(paste0(version_LS_trans,"_Q2_Landscape01.tif")),'LSQ202' = c(paste0(version_LS_trans, "_Q2_Landscape02.tif")),'LSQ203' = c(paste0(version_LS_trans,"_Q2_Landscape03.tif")),'LSQ204' = c(paste0(version_LS_trans,"_Q2_Landscape04.tif")),'LSQ205' = c(paste0(version_LS_trans,"_Q2_Landscape05.tif")))


Q3<-  list('LSQ301' = c(paste0(version_LS_trans,"_Q3_Landscape01.tif")),'LSQ302' = c(paste0(version_LS_trans, "_Q3_Landscape02.tif")),'LSQ303' = c(paste0(version_LS_trans,"_Q3_Landscape03.tif")),'LSQ304' = c(paste0(version_LS_trans,"_Q3_Landscape04.tif")),'LSQ305' = c(paste0(version_LS_trans,"_Q3_Landscape05.tif")))


Q4 <-  list('LSQ401' = c(paste0(version_LS_trans,"_Q4_Landscape01.tif")),'LSQ402' = c(paste0(version_LS_trans, "_Q4_Landscape02.tif")),'LSQ403' = c(paste0(version_LS_trans,"_Q4_Landscape03.tif")),'LSQ404' = c(paste0(version_LS_trans,"_Q4_Landscape04.tif")),'LSQ405' = c(paste0(version_LS_trans,"_Q4_Landscape05.tif")))


LS_trans<-do.call(c,(list(NL,Q1, Q2, Q3, Q4,RT))) 
```

### ZONAL HISTOGRAM 
####For one scenario at a time. See code below for all scenarios 
Note: run on final landscape 

```{r warning= FALSE, message= FALSE, eval=FALSE}

old <- Sys.time() # TIMING SCRIPT
for(in_to_fin in names(LS_trans)){
  
Final_Landscape <-paste0(inRasterLoc, LS_trans[[in_to_fin]][1]) #full file path using inRasterLoc as the base

Final_hist_output <- paste0(Comb_output, gsub(".img","_hist.txt",LS_trans[[in_to_fin]][1])) #naming the file output. Taking the name of the raster to make the name of the output table. Remove tif. put _hist.txt

Final_Landscape <- raster(Final_Landscape) #full file path using inRasterLoc as the base
fin_vals <- getValues(Final_Landscape) 

final <- ifelse(fin_vals %in%  c("3","5","6","7"), fin_vals, 0) #select desired transitions 

final <- paste0(final, ".", counties_vals)

final_hist0 <- summary(factor(final), maxsum = length(unique(final)))# had to add mmaxsum = length(unique(final)) because otherwise doesn't show all possible values and there is a column called "others" - Val

final_hist0 <- final_hist0[-grep("^(-?)0.", names(final_hist0))] #remove values that we don't want

#create table with county as row, landuse as column
final_hist <- sa_ctyGEOID 

for(i in final_hist$Din_cty){
 
 for (j in c("3","5","6","7")){ 
   if(any(names(final_hist0) == paste(j, i, sep = "."))){
     final_hist[final_hist$Din_cty == i, as.character(j)] <- final_hist0[names(final_hist0) == paste(j, i, sep = ".")]
   }}}

final_hist <- t(final_hist[-1])
colnames(final_hist) <- paste0("GEOID_", final_hist[1,])
final_hist <- final_hist[-1,]
final_hist <- cbind(data.frame(Rowid_ = 1:nrow(final_hist),LABEL = rownames(final_hist)), final_hist)
final_hist<-arrange(final_hist, LABEL)   

final_hist[is.na(final_hist)]<-0

#WRITE TO FILE 
write.table(final_hist, file = Final_hist_output, row.names=FALSE, col.names=TRUE, sep=",")  

}

new<-Sys.time()-old 
print(new)
```

###ZONAL HISTOGRAM ALL SCENARIOS 
#### Loops through all scenarios. 

```{r, eval=FALSE}
old <- Sys.time() # TIMING SCRIPT

InRasterLoc_LsTrans<-paste0(inRasterLoc, LS_trans)


for(i in 1:length(InRasterLoc_LsTrans)){ 
  Final_hist_output <- paste0(Comb_output,gsub(".tif","_hist.txt",LS_trans[[i]][1])) 
  Final_Landscape <- raster(InRasterLoc_LsTrans[[i]][1]) 
  fin_vals <- getValues(Final_Landscape) 
  

  final <- ifelse(fin_vals %in%  c("3","5","6","7"), fin_vals, 0)
  

  final <- paste0(final, ".", counties_vals)

  final_hist0 <- summary(factor(final), maxsum = length(unique(final))) 
  

  final_hist0 <- final_hist0[-grep("^(-?)0.", names(final_hist0))]
  

  final_hist <- sa_ctyGEOID
  
  for(i in final_hist$Din_cty){
    
    for (j in c("3","5","6","7")){ 
      if(any(names(final_hist0) == paste(j, i, sep = "."))){
        final_hist[final_hist$Din_cty == i, as.character(j)] <- final_hist0[names(final_hist0) == paste(j, i, sep = ".")]
      }}}
  

  final_hist <- t(final_hist[-1])
  colnames(final_hist) <- paste0("GEOID_", final_hist[1,])
  final_hist <- final_hist[-1,]
  final_hist <- cbind(data.frame(Rowid_ = 1:nrow(final_hist),LABEL = rownames(final_hist)), final_hist)
  final_hist<-arrange(final_hist, LABEL)   
  

  final_hist[is.na(final_hist)]<-0
  

  # WRITE TO FILE
  write.table(final_hist, file = Final_hist_output, row.names=FALSE, col.names=TRUE, sep=",")  
}

new<-Sys.time()-old # TIMING SCRIPT
print(new)
```
