---
title: "Scholarly Studies Bee and Mammal Data"
output:
  html_document: 
    toc: yes
  pdf_document: default
editor_options:
  chunk_output_type: console
---

This RMarkdown document is the data exploration for apidae bee data (subset by VWL) and emammal data (Mike Cove). Explored are the relationship between species abundance and species richness with land use change metrics. The land use change metrics are at four scales (250 m, 500m, 1000m, 5000m). The goal is to see if there is a relationship between these biodiversity surrogates and land use change metrics to include in the proposal for scholarly studies. Ultimately, we are looking to create an SEM that determines the naturalness of the area. 

#Packages 
```{r message=FALSE, warning=FALSE}
setwd("U:/CLI/Field Surveys/")

library(vegan) #diversity index
library(picante)
library(dplyr) #tibbles and data manipulation
library(tidyr) #transpose data
library(knitr) #print tables in R Markdown
library(ggplot2)
library(lubridate)#manipulate date-time data
library(lattice)
library(gridExtra)
library(reshape2)
```


##Bee
```{r}

data<-read.csv("U:/CLI/Field Surveys/Bees/Data/apidae_subset_bluevane_bee_data_2014_2017_CF_OneYearsData.csv",header=TRUE)
data$Date_collected<-as.POSIXct(data$Date_collected,format="%m/%d/%Y")

SummaryData<-data%>%group_by(Year,Lat,Lon,SiteLocatC,Family_species)%>% #group by site and spp
  summarize(Abundance=sum(Number_of_specimens))%>% #sum abundance of each spp by site
  spread(Family_species, Abundance)%>% #transpose
  replace(is.na(.), 0)

SummaryData_Abund<-SummaryData[,-c(1:3)]
SummaryData_Abund$SiteLocatC<-as.character(SummaryData_Abund$SiteLocatC)
SummaryData_Abund<-mutate(SummaryData_Abund,SpRichness=specnumber(SummaryData_Abund))
SummaryData_Abund$SpRichness<-SummaryData_Abund$SpRichness-1

data<-left_join(SummaryData[,c(1:4)], SummaryData_Abund,by="SiteLocatC")


#write.csv(data, "U:/CLI/Field Surveys/Bees/Data/CLI_bee_data_sprichness.csv", row.names = FALSE)
```

Bring in Data created in ArcMap
```{r}
dataE<-read.csv("U:/CLI/Field Surveys/Bees/Data/CLI_bee_environmental.csv")

data<-left_join(data, dataE[,c(5,18,20:35)], by="SiteLocatC")
```

View Datasets
```{r echo=FALSE, results='asis'}
#kable(data,caption="Bee Abundance and Land Use Variables")

```

###Histograms of Bees and Variables 

```{r}
#Abundance Histogram
#over 0 because in first bin 0-20
ggplot(gather(data[,18]), aes(value)) + 
    geom_histogram(bins = 20) + 
    facet_wrap(~key, scales = 'free_x')+
    xlab("Number of individuals per site")+
    ylab("Number of Sites")
#Species Richness Histogram
ggplot(gather(data[,17]), aes(value)) + 
    geom_histogram(bins = 20) + 
    facet_wrap(~key, scales = 'free_x')+
    xlab("Number of species per site")+
    ylab("Number of Sites")


#Land Use
ggplot(gather(data[,19:34]), aes(value)) + 
    geom_histogram(bins = 20) + 
    facet_wrap(~key, scales = 'free_x')+
    ylab("Number of Sites")+
    xlab("Percent of Land use")



```

###Bar Graphs
####Abudance
```{r}
data_Abund_subset<-data[,c(4,18:34)]
data_Abund_subset<-as.data.frame(data_Abund_subset)
data_melt<-melt(data_Abund_subset, id=c("SiteLocatC", "Abundance"))

data_melt_250<-subset(data_melt, variable==c("dev_250", "for_250", "cro_250", "gra_250"))
data_melt_500<-subset(data_melt, variable==c("dev_500", "for_500", "cro_500", "gra_500"))
data_melt_1000<-subset(data_melt, variable==c("dev_1000", "for_1000", "cro_1000", "gra_1000"))
data_melt_5000<-subset(data_melt, variable==c("dev_5000", "for_5000", "cro_5000", "gra_5000"))

ggplot(data_melt_250, aes(y=Abundance, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Abundance (Number of Individuals)")

ggplot(data_melt_500, aes(y=Abundance, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Abundance (Number of Individuals)")
         
 ggplot(data_melt_1000, aes(y=Abundance, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Abundance (Number of Individuals)")
         
ggplot(data_melt_5000, aes(y=Abundance, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Abundance (Number of Individuals)")
         
```

####Species Richness
```{r}
data_Richness_subset<-data[,c(4,17,19:34)]
data_Richness_subset<-as.data.frame(data_Richness_subset)
data_meltR<-melt(data_Richness_subset, id=c("SiteLocatC", "SpRichness"))

data_meltR_250<-subset(data_meltR, variable==c("dev_250", "for_250", "cro_250", "gra_250"))
data_meltR_500<-subset(data_meltR, variable==c("dev_500", "for_500", "cro_500", "gra_500"))
data_meltR_1000<-subset(data_meltR, variable==c("dev_1000", "for_1000", "cro_1000", "gra_1000"))
data_meltR_5000<-subset(data_meltR, variable==c("dev_5000", "for_5000", "cro_5000", "gra_5000"))

ggplot(data_meltR_250, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")

ggplot(data_meltR_500, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")
         
 ggplot(data_meltR_1000, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")
         
ggplot(data_meltR_5000, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")
         
```


###Correlation

```{r}
#250 meters
pairs(data[c(17:22)])

#500 meters
pairs(data[c(17,18,23,24,25,26)])

#1000 meters (1km)
pairs(data[c(17,18,27,28,29,30)])

#5000 meters (5km)
pairs(data[c(17,18,31,32,33,34)])
```

###Q-Q Plots
```{r}
apply(data[5:34], 2, function(i){
  qqnorm(i)
})

```


### Exploratory Plots

```{r, eval=FALSE}
ggplotRegression <- function(fit){
  ggplot(fit$model,aes_string(x=names(fit$model)[2],y=names(fit$model)[1]))+
    geom_point()+
    stat_smooth(method="lm", col="red")+
    labs(title=paste("Adj R2 = ", signif(summary(fit)$adj.r.squared,5),
                     "Intercept = ", signif(fit$coef[[1]],5),
                     "Slope = ", signif(fit$coef[[2]],5),
                     "P-value = ",signif(summary(fit)$coef[2,4],5)))
}

#250 meters
dev_250<-ggplotRegression(glm(data$SpRichness ~ data$dev_250, family="poisson" ))
for_250<-ggplotRegression(glm(data$SpRichness ~ data$for_250, family="poisson"))
cro_250<-ggplotRegression(glm(data$SpRichness ~ data$cro_250, family="poisson"))
gra_250<-ggplotRegression(glm(data$SpRichness ~ data$gra_250, family="poisson"))

grid.arrange(dev_250, for_250, cro_250, gra_250, ncol=2)

#development 
summary(lm(data$SpRichness ~ data$dev_250, family="poisson"))
#forest
summary(lm(data$SpRichness ~ data$for_250, family="poisson"))
#crop
summary(lm(data$SpRichness ~ data$cro_250, family="poisson"))
#grass
summary(lm(data$SpRichness ~ data$gra_250, family="poisson"))

#500 meters
dev_500<-ggplotRegression(glm(data$SpRichness ~ data$dev_500, family="poisson"))
for_500<-ggplotRegression(glm(data$SpRichness ~ data$for_500, family="poisson"))
cro_500<-ggplotRegression(glm(data$SpRichness ~ data$cro_500, family="poisson"))
gra_500<-ggplotRegression(glm(data$SpRichness ~ data$gra_500, family="poisson"))

grid.arrange(dev_500, for_500, cro_500, gra_500, ncol=2)

#development 
summary(glm(data$SpRichness ~ data$dev_500, family="poisson"))
#forest
summary(glm(data$SpRichness ~ data$for_500, family="poisson"))
#crop
summary(glm(data$SpRichness ~ data$cro_500, family="poisson"))
#grass
summary(glm(data$SpRichness ~ data$gra_500, family="poisson"))

#1000 meters (1km)
dev_1000<-ggplotRegression(glm(data$SpRichness ~ data$dev_1000, family="poisson"))
for_1000<-ggplotRegression(glm(data$SpRichness ~ data$for_1000, family="poisson"))
cro_1000<-ggplotRegression(glm(data$SpRichness ~ data$cro_1000, family="poisson"))
gra_1000<-ggplotRegression(glm(data$SpRichness ~ data$gra_1000, family="poisson"))

grid.arrange(dev_1000, for_1000, cro_1000, gra_1000, ncol=2)

#development 
summary(glm(data$SpRichness ~ data$dev_1000, family="poisson"))
#forest
summary(glm(data$SpRichness ~ data$for_1000, family="poisson"))
#crop
summary(glm(data$SpRichness ~ data$cro_1000, family="poisson"))
#grass
summary(glm(data$SpRichness ~ data$gra_1000, family="poisson"))

#5000 meters (5km)
dev_5000<-ggplotRegression(glm(data$SpRichness ~ data$dev_5000, family="poisson"))
for_5000<-ggplotRegression(glm(data$SpRichness ~ data$for_5000, family="poisson"))
cro_5000<-ggplotRegression(glm(data$SpRichness ~ data$cro_5000, family="poisson"))
gra_5000<-ggplotRegression(glm(data$SpRichness ~ data$gra_5000, family="poisson"))

grid.arrange(dev_5000, for_5000, cro_5000, gra_5000, ncol=2)

#development 
summary(glm(data$SpRichness ~ data$dev_5000, family="poisson"))
#forest
summary(glm(data$SpRichness ~ data$for_5000, family="poisson"))
#crop
summary(glm(data$SpRichness ~ data$cro_5000, family="poisson"))
#grass
summary(glm(data$SpRichness ~ data$gra_5000, family="poisson"))
```
#Mammal 
```{r}
dataraw<-read.csv("U:/CLI/Field Surveys/eMammal/RAW_Urban_to_Wild_data.csv",header=TRUE)

dataraw_Abund<-dataraw%>%group_by(Year,Deployment,Year,Species.Name, Lat, Long)%>% #group by site and spp
  summarize(Abundance=sum(Count))%>% #sum abundance of each spp by site
  spread(Species.Name, Abundance)%>% #transpose
  replace(is.na(.), 0)

#write.csv(dataraw_Abund, "U:/CLI/Field Surveys/eMammal/CLI_mammal_dat_habitat_SH.csv")
```


`##Mammal Native
```{r}

data<-read.csv("U:/CLI/Field Surveys/eMammal/CLI_mammal_environmental_native.csv",header=TRUE) 
data<-subset(data, Abundance > 0)
Data_Abund<-data[,-c(2,3,4,21:37)] #only abundance 
Data_Abund$Deployment<-as.character(Data_Abund$Deployment)
Data_Abund<-Data_Abund%>%replace(is.na(.), 0)

Data_Abund<-mutate(Data_Abund, SpRichness=specnumber(Data_Abund))
Data_Abund$SpRichness<-Data_Abund$SpRichness-2

dataM<-semi_join(data[,c(1,2,3,4,5,6,21:36)],Data_Abund, by=c("Deployment", "Lat", "Long"))#Combined back to data 
```


View dataM 
```{r echo=FALSE, results='asis'}
#kable(dataM,caption="Mammal Abundance and Land Use Variables")

```

###Histograms of Native Mammals and Variables 



```{r}
#Species Richness 
ggplot(gather(dataM[38]), aes(value)) + 
    geom_histogram(bins = 20) + 
    facet_wrap(~key, scales = 'free_x')+
    xlab("Number of species per site")+
    ylab("Number of Sites")
#Land Use
ggplot(gather(dataM[,8:23]), aes(value)) + 
    geom_histogram(bins = 20) + 
    facet_wrap(~key, scales = 'free_x')+
   ylab("Number of Sites")+
    xlab("Percent of land use")
```

###Bar Graphs 


####Species  Richness
```{r}
dataM_richness_subset<-dataM[,c(2,38,8:23)]
dataM_richness_subset<-as.data.frame(dataM_richness_subset)
dataM_meltR<-melt(dataM_richness_subset, id=c("Deployment", "SpRichness"))

dataM_meltR_250<-subset(dataM_meltR, variable==c("dev_250", "for_250", "cro_250", "gra_250"))
dataM_meltR_500<-subset(dataM_meltR, variable==c("dev_500", "for_500", "cro_500", "gra_500"))
dataM_meltR_1000<-subset(dataM_meltR, variable==c("dev_1000", "for_1000", "cro_1000", "gra_1000"))
dataM_meltR_5000<-subset(dataM_meltR, variable==c("dev_5000", "for_5000", "cro_5000", "gra_5000"))

ggplot(dataM_meltR_250, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")

ggplot(dataM_meltR_500, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")
         
 ggplot(dataM_meltR_1000, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")
         
ggplot(dataM_meltR_5000, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")
```

###Correlation

```{r}
#250 meters
pairs(dataM[c(8:11,38)])

#500 meters
pairs(dataM[c(38,12:15)])

#1000 meters (1km)
pairs(dataM[c(38,16:19)])

#5000 meters (5km)
pairs(dataM[c(38,20:23)])
```

```{r}
apply(dataM[5:34], 2, function(i){
  qqnorm(i)
})

```

### Exploratory Plots

```{r, eval=FALSE}
ggplotRegression <- function(fit){
  ggplot(fit$model,aes_string(x=names(fit$model)[2],y=names(fit$model)[1]))+
    geom_point()+
    stat_smooth(method="lm", col="red")+
    labs(title=paste("Adj R2 = ", signif(summary(fit)$adj.r.squared,5),
                     "Intercept = ", signif(fit$coef[[1]],5),
                     "Slope = ", signif(fit$coef[[2]],5),
                     "P-value = ",signif(summary(fit)$coef[2,4],5)))
}

#250 meters
dev_250<-ggplotRegression(glm(dataM$SpRichness ~ dataM$dev_250, family="poisson"))
for_250<-ggplotRegression(glm(dataM$SpRichness ~ dataM$for_250, family="poisson"))
cro_250<-ggplotRegression(glm(dataM$SpRichness ~ dataM$cro_250, family="poisson"))
gra_250<-ggplotRegression(glm(dataM$SpRichness ~ dataM$gra_250, family="poisson"))

grid.arrange(dev_250, for_250, cro_250, gra_250, ncol=2)

#development 
summary(glm(dataM$SpRichness ~ dataM$dev_250, family="poisson"))
#forest
summary(glm(dataM$SpRichness ~ dataM$for_250, family="poisson"))
#crop
summary(glm(dataM$SpRichness ~ dataM$cro_250, family="poisson"))
#grass
summary(glm(dataM$SpRichness ~ dataM$gra_250, family="poisson"))

#500 meters
dev_500<-ggplotRegression(glm(dataM$SpRichness ~ dataM$dev_500, family="poisson"))
for_500<-ggplotRegression(glm(dataM$SpRichness ~ dataM$for_500, family="poisson"))
cro_500<-ggplotRegression(glm(dataM$SpRichness ~ dataM$cro_500, family="poisson"))
gra_500<-ggplotRegression(glm(dataM$SpRichness ~ dataM$gra_500, family="poisson"))

grid.arrange(dev_500, for_500, cro_500, gra_500, ncol=2)

#development 
summary(glm(dataM$SpRichness ~ dataM$dev_500, family="poisson"))
#forest
summary(glm(dataM$SpRichness ~ dataM$for_500, family="poisson"))
#crop
summary(glm(dataM$SpRichness ~ dataM$cro_500, family="poisson"))
#grass
summary(glm(dataM$SpRichness ~ dataM$gra_500, family="poisson"))

#1000 meters (1km)
dev_1000<-ggplotRegression(glm(dataM$SpRichness ~ dataM$dev_1000, family="poisson"))
for_1000<-ggplotRegression(glm(dataM$SpRichness ~ dataM$for_1000, family="poisson"))
cro_1000<-ggplotRegression(glm(dataM$SpRichness ~ dataM$cro_1000, family="poisson"))
gra_1000<-ggplotRegression(glm(dataM$SpRichness ~ dataM$gra_1000, family="poisson"))

grid.arrange(dev_1000, for_1000, cro_1000, gra_1000, ncol=2)


#development 
summary(glm(dataM$SpRichness ~ dataM$dev_1000, family="poisson"))
#forest
summary(glm(dataM$SpRichness ~ dataM$for_1000, family="poisson"))
#crop
summary(glm(dataM$SpRichness ~ dataM$cro_1000, family="poisson"))
#grass
summary(glm(dataM$SpRichness ~ dataM$gra_1000, family="poisson"))

#5000 meters (5km)
dev_5000<-ggplotRegression(glm(dataM$SpRichness ~ dataM$dev_5000, family="poisson"))
for_5000<-ggplotRegression(glm(dataM$SpRichness ~ dataM$for_5000, family="poisson"))
cro_5000<-ggplotRegression(glm(dataM$SpRichness ~ dataM$cro_5000, family="poisson"))
gra_5000<-ggplotRegression(glm(dataM$SpRichness ~ dataM$gra_5000, family="poisson"))

grid.arrange(dev_5000, for_5000, cro_5000, gra_5000, ncol=2)

#development 
summary(glm(dataM$SpRichness ~ dataM$dev_5000, family="poisson"))
#forest
summary(glm(dataM$SpRichness ~ dataM$for_5000, family="poisson"))
#crop
summary(glm(dataM$SpRichness ~ dataM$cro_5000, family="poisson"))
#grass
summary(glm(dataM$SpRichness ~ dataM$gra_5000, family="poisson"))

```

##Mammal Non-Native 
```{r}

data<-read.csv("U:/CLI/Field Surveys/eMammal/CLI_mammal_environmental_nonnative.csv",header=TRUE) 
data<-subset(data, Abundance > 0)
Data_Abund<-data[,-c(2,3,4,11:28)] #only abundance 
Data_Abund$Deployment<-as.character(Data_Abund$Deployment)
#Data_Abund<-Data_Abund%>%replace(is.na(.), 0)

Data_Abund<-mutate(Data_Abund, SpRichness=specnumber(Data_Abund))
Data_Abund$SpRichness<-Data_Abund$SpRichness-2

dataMN<-semi_join(data[,c(1:6,11:28)],Data_Abund, by=c("Deployment", "Lat", "Long"))#Combined back to data 
```


View dataMN 
```{r echo=FALSE, results='asis'}
#kable(dataMN,caption="Mammal Abundance and Land Use Variables")

```

###Histograms of Non Native Mammals and Variables 



```{r}
#Species Richness 
ggplot(gather(dataMN[28]), aes(value)) + 
    geom_histogram(bins = 20) + 
    facet_wrap(~key, scales = 'free_x')+
    xlab("Number of species per site")+
    ylab("Number of Sites")
#Land Use
ggplot(gather(dataMN[,8:23]), aes(value)) + 
    geom_histogram(bins = 20) + 
    facet_wrap(~key, scales = 'free_x')+
   ylab("Number of Sites")+
    xlab("Percent of land use")

```

###Bar Graphs 

####Species Richness
```{r}
dataMN_richness_subset<-dataMN[,c(2,28,8:23)]
dataMN_richness_subset<-as.data.frame(dataMN_richness_subset)
dataMN_meltR<-melt(dataMN_richness_subset, id=c("Deployment", "SpRichness"))

dataMN_meltR_250<-subset(dataMN_meltR, variable==c("dev_250", "for_250", "cro_250", "gra_250"))
dataMN_meltR_500<-subset(dataMN_meltR, variable==c("dev_500", "for_500", "cro_500", "gra_500"))
dataMN_meltR_1000<-subset(dataMN_meltR, variable==c("dev_1000", "for_1000", "cro_1000", "gra_1000"))
dataMN_meltR_5000<-subset(dataMN_meltR, variable==c("dev_5000", "for_5000", "cro_5000", "gra_5000"))

ggplot(dataMN_meltR_250, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")

ggplot(dataMN_meltR_500, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")
         
 ggplot(dataMN_meltR_1000, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")
         
ggplot(dataMN_meltR_5000, aes(y=SpRichness, x=value, width=.1))+
         geom_bar(stat="identity", position="identity")+
         facet_grid(.~variable)+
          xlab("Percent of Land Use")+
         ylab("Species Richness (Number of Species)")
```



###Correlation

```{r}
#250 meters
pairs(dataMN[c(8:11,28)])

#500 meters
pairs(dataMN[c(28,12:15)])

#1000 meters (1km)
pairs(dataMN[c(28,16:19)])

#5000 meters (5km)
pairs(dataMN[c(28,20:23)])
```

```{r}
apply(dataMN[5:34], 2, function(i){
  qqnorm(i)
})
```

### Exploratory Plots

```{r, eval=FALSE}
ggplotRegression <- function(fit){
  ggplot(fit$model,aes_string(x=names(fit$model)[2],y=names(fit$model)[1]))+
    geom_point()+
    stat_smooth(method="lm", col="red")+
    labs(title=paste("Adj R2 = ", signif(summary(fit)$adj.r.squared,5),
                     "Intercept = ", signif(fit$coef[[1]],5),
                     "Slope = ", signif(fit$coef[[2]],5),
                     "P-value = ",signif(summary(fit)$coef[2,4],5)))
}

#250 meters
dev_250<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$dev_250, family="poisson"))
for_250<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$for_250, family="poisson"))
cro_250<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$cro_250, family="poisson"))
gra_250<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$gra_250, family="poisson"))

grid.arrange(dev_250, for_250, cro_250, gra_250, ncol=2)

#development 
summary(glm(dataMN$SpRichness ~ dataMN$dev_250, family="poisson"))
#forest
summary(glm(dataMN$SpRichness ~ dataMN$for_250, family="poisson"))
#crop
summary(glm(dataMN$SpRichness ~ dataMN$cro_250, family="poisson"))
#grass
summary(glm(dataMN$SpRichness ~ dataMN$gra_250, family="poisson"))

#500 meters
dev_500<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$dev_500, family="poisson"))
for_500<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$for_500, family="poisson"))
cro_500<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$cro_500, family="poisson"))
gra_500<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$gra_500, family="poisson"))

grid.arrange(dev_500, for_500, cro_500, gra_500, ncol=2)

#development 
summary(glm(dataMN$SpRichness ~ dataMN$dev_500, family="poisson"))
#forest
summary(glm(dataMN$SpRichness ~ dataMN$for_500, family="poisson"))
#crop
summary(glm(dataMN$SpRichness ~ dataMN$cro_500, family="poisson"))
#grass
summary(glm(dataMN$SpRichness ~ dataMN$gra_500, family="poisson"))

#1000 meters (1km)
dev_1000<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$dev_1000, family="poisson"))
for_1000<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$for_1000, family="poisson"))
cro_1000<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$cro_1000, family="poisson"))
gra_1000<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$gra_1000, family="poisson"))

grid.arrange(dev_1000, for_1000, cro_1000, gra_1000, ncol=2)


#development 
summary(glm(dataMN$SpRichness ~ dataMN$dev_1000, family="poisson"))
#forest
summary(glm(dataMN$SpRichness ~ dataMN$for_1000, family="poisson"))
#crop
summary(glm(dataMN$SpRichness ~ dataMN$cro_1000, family="poisson"))
#grass
summary(glm(dataMN$SpRichness ~ dataMN$gra_1000, family="poisson"))

#5000 meters (5km)
dev_5000<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$dev_5000, family="poisson"))
for_5000<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$for_5000, family="poisson"))
cro_5000<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$cro_5000, family="poisson"))
gra_5000<-ggplotRegression(glm(dataMN$SpRichness ~ dataMN$gra_5000, family="poisson"))

grid.arrange(dev_5000, for_5000, cro_5000, gra_5000, ncol=2)

#development 
summary(glm(dataMN$SpRichness ~ dataMN$dev_5000, family="poisson"))
#forest
summary(glm(dataMN$SpRichness ~ dataMN$for_5000, family="poisson"))
#crop
summary(glm(dataMN$SpRichness ~ dataMN$cro_5000, family="poisson"))
#grass
summary(glm(dataMN$SpRichness ~ dataMN$gra_5000, family="poisson"))

```
