---
title: "Significant Metrics Regressions"
output:
  html_document: 
    toc: yes
editor_options:
  chunk_output_type: console
---
#Packages 
```{r message=FALSE, warning=FALSE}
setwd("U:/CLI/Field Surveys/MultiTaxaProducts/")

library(vegan) #diversity index
library(picante)
library(dplyr) #tibbles and data manipulation
library(tidyr) #transpose data
library(knitr) #print tables in R Markdown
library(ggplot2)
library(lubridate)#manipulate date-time data
library(lattice)
library(gridExtra)
library(reshape2)
library(sandwich)
```
#INTRODUCTION
IGNORE THE P-VALUES ON THE GRAPHS THESE DO NOT REFLECT ROBUST STANDAND ERRORS AND ROBUST P-VALUES. 
https://stats.idre.ucla.edu/r/dae/poisson-regression/

#Bee Data
```{r}
data<-read.csv("U:/CLI/Field Surveys/Bees/Data/CLI_bee_CF_8-22-18.csv")
```

##General Linear Regression- Bee Species Richness 
```{r}
ggplotRegression<- function(fit){
  ggplot(fit$model,aes_string(x=names(fit$model)[2],y=names(fit$model)[1]))+
   geom_point()+
    stat_smooth(method="glm", col="red")+
    labs(title=paste(#"Adj R2 = ", signif(summary(fit)$adj.r.squared,5),
                     "Intercept = ", signif(fit$coef[[1]],5),
                    "Slope = ", signif(fit$coef[[2]],5),
                     "P-value = ",signif(summary(fit)$coef[2,4],5)))
}
```

###Bee Richness and Percent of Development within 250m 
```{r}
ggplotRegression(glm(data$SpRichness ~ data$dev_250, family="poisson"))
```


#Bird Data
```{r}
dataB<-read.csv("U:/CLI/Field Surveys/Birds/Birds_Pre2018_join.csv")
dataB[dataB=="-9999"]<-NA
```
##General Linear Regression- Bird Species Richness

###Bird Richness and Percent of Grass within 500m 
```{r}
ggplotRegression(glm(dataB$Bird_Richness ~ dataB$gra_500, family="poisson"))
```


###Bird Richness and Percent of Grass within 1000m 
```{r}
ggplotRegression(glm(dataB$Bird_Richness ~ dataB$gra_1000, family="poisson"))
```

###Bird Richness and Percent of Grass within 5000m 
```{r}
ggplotRegression(glm(dataB$Bird_Richness ~ dataB$gra_5000, family="poisson"))
```

###Bird Richness and Percent of Core Grass within 500m
```{r}
ggplotRegression(glm(dataB$Bird_Richness ~ dataB$P_GraC_500, family="poisson"))
```

###Bird Richness and Percent of Core Grass within 1000m 
```{r}
ggplotRegression(glm(dataB$Bird_Richness ~ dataB$P_GraC_1k, family="poisson"))
```

###Bird Richness and Percent of Core Grass within 5000m 
```{r}
ggplotRegression(glm(dataB$Bird_Richness ~ dataB$P_GraC_5k, family="poisson"))
```

#Invasive Data
```{r}
dataI<-read.csv("U:/CLI/Field Surveys/Invasive/SchSt_Invasive_Grid_join.csv",header=TRUE)
dataI[dataI=="-9999"]<-NA
```

##General Linear Model-Invasive Abundance 

###Invasive Abundance and Percent of Development within 500m 
```{r}
ggplotRegression(glm(dataI$Sum_Woody ~ dataI$dev_500, family="poisson"))
```

#Native Mammal Data 
```{r}
dataM<-read.csv("U:/CLI/Field Surveys/eMammal/CLI_NativeMammal_8-22-18.csv")
```

##General Linear Model-Native Mammal Richness 
###Native Mammal Richness and Percent of Grass within 500m 
```{r}
ggplotRegression(glm(dataM$SpRichness ~ dataM$gra_500, family="poisson"))
```

###Native Mammal Richness and Percent of Grass within 1000m 
```{r}
ggplotRegression(glm(dataM$SpRichness ~ dataM$gra_1000, family="poisson"))
```

###Native Mammal Richness and Percent of Grass within 5000m 
```{r}
ggplotRegression(glm(dataM$SpRichness ~ dataM$gra_5000, family="poisson"))
```

###Native Mammal Richness and Percent of Core Grass within 500m 
```{r}
ggplotRegression(glm(dataM$SpRichness ~ dataM$P_GraC_500, family="poisson"))
```

###Native Mammal Richness and Percent of Core Grass within 1000m 
```{r}
ggplotRegression(glm(dataM$SpRichness ~ dataM$P_GraC_1k, family="poisson"))
```

###Native Mammal Richness and Percent of Core Grass within 5000m 
```{r}
ggplotRegression(glm(dataM$SpRichness ~ dataM$P_GraC_5k, family="poisson")) 

```
