---
title: "ForestPatches_8-2-2018"
author: "Sarah Halperin"
date: "August 10, 2018"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

##INTRODUCTION

###Packages Needed 
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(raster) # read and edit rasters
library(SDMTools) # Species Distribution Modelling Tools
library(Hmisc)  # useful functions for data analysis
library(rgdal)  # Add this package to read .tif files
library(igraph) # Run function clump().
library(dplyr) # !! Remove dplyr in order to run clump detach(name="package:dplyr", unload=TRUE)
```

###File Paths (may have to update slightly for desired outcome)
```{r, eval=FALSE}
version<-"/StudyArea_V201/SA_V2016"
version_input<-paste0("U:/CLI/Dinamica_Runs",version, "/FutureLandscapes/")
version_output<-"BasicDataAnalyses/Forest_Stats/County/"
Output_Folder<-gsub("FutureLandscapes/", version_output, version_input)

RasterLoc <- version_input
```

```{r, eval=FALSE}
PL_GAP<-paste0("U:/CLI/Dinamica_Runs",version, "/FutureLandscapes/PL_GAP/")
Output_Folder<-gsub("FutureLandscapes/", version_output, PL_GAP)
```

###Read in input files 

```{r, eval=FALSE}
# COUNTY RASTERS:
counties<- raster(paste(cntyRasterLoc, "cnty_an", ".img", sep="")) # this is for the raster. 
```

Study Area Mask 
```{r, eval=FALSE}
cnty_saMASK<-raster("U:/CLI/PreparedRasters/StudyAreaBndy/cnty_saMASK.tif") 
```

County Area Mask 
```{r, eval=FALSE}
county_trans<-"U:/CLI/SpatialData/VAClipRaw/VA_NRCS/CountiesEd/Indv/TIF_SA/"
county_saMaskList <-  list('Augusta' = c(paste0(county_trans,"aug_stau_wayn.img")),'Rockingham' = c(paste0(county_trans, "rock_harr.img")),'Albemarle' = c(paste0(county_trans,"albe_charl.img")),'Frederick' = c(paste0(county_trans,"fred_win.img")),'Clarke' = c(paste0(county_trans,"clarke.img")),'Fauquier' = c(paste0(county_trans,"fauquier.img")),'Page' = c(paste0(county_trans,"page.img")),'Culpeper' = c(paste0(county_trans,"culpeper.img")),'greene' = c(paste0(county_trans,"greene.img")),'loudon' = c(paste0(county_trans,"loudon.img")),'madison' = c(paste0(county_trans,"madison.img")),'orange' = c(paste0(county_trans,"orange.img")),'rappahannock' = c(paste0(county_trans,"raphanock.img")),'shenandoah' = c(paste0(county_trans,"shenandoah.img")),'warren' = c(paste0(county_trans,"warren.img")))
```

Region Area Mask 
```{r, eval=FALSE}
region_trans<-"U:/CLI/SpatialData/VAClipRaw/VA_NRCS/Regions/" 
region_saMaskList<-list('1' = c(paste0(region_trans,"region_1.img")),'2' = c(paste0(region_trans, "region_2.img")),'3' = c(paste0(region_trans,"region_3.img")),'4' = c(paste0(region_trans,"region_4.img")),'5' = c(paste0(region_trans,"region_5.img")),'6' = c(paste0(region_trans,"region_6.img")),'7' = c(paste0(region_trans,"region_7.img")),'8' = c(paste0(region_trans,"region_8.img")))
```

```{r, eval=FALSE}
regions_StudyArea<-raster("U:/CLI/PreparedRasters/StudyAreaBndy/ctny_StudyArea.tif")
studyarea_vals <- getValues(regions_StudyArea) #the file represents counties (3-56)


# County Tables:
S20_GEOID<- read.table("U:/CLI/Dinamica_Runs/StudyArea_V201/SAcntyOnly.csv", header = T, sep=",")
colnames(S20_GEOID)<-c("VALUE", "GEOID", "Name")
```

##CODE BEGINS 

###List files to read in 

```{r,, eval=FALSE}
LS_trans <-  list(
 'NL01' = list(
   'xx01' = c("NL/nlcd_nlcd/nlcd01_anC.tif", "NL/nlcd_nlcd/nlcd01_anC.tif")), 
 'NL11' = list(
  '0111' = c("NL/nlcd_nlcd/nlcd11_anC.tif", "NL/nlcd_nlcd/nlcd11_anC.tif")), 
 'RT05'= list(
   'xxRT'= c(paste0("RT/", version_LS_trans,"_RT", "_Landscape05.tif") ,paste0("RT/", version_LS_trans, "_RT", "_Landscape05.tif"))), 
    'Q105'= list(
     'xxQ1'= c(paste0("Q1/", version_LS_trans, "_Q1", "_Landscape05.tif") ,paste0("Q1/", version_LS_trans, "_Q1", "_Landscape05.tif"))),
     'Q205'= list(
      'xxQ2'= c(paste0("Q2/", version_LS_trans, "_Q2", "_Landscape05.tif") ,paste0("Q2/", version_LS_trans, "_Q2", "_Landscape05.tif"))),
  'Q305'= list(
    'xxQ3'= c(paste0("Q3/", version_LS_trans, "_Q3", "_Landscape05.tif") ,paste0("Q3/", version_LS_trans, "_Q3", "_Landscape05.tif"))),
 'Q405'= list(
    'xxQ4'= c(paste0("Q4/", version_LS_trans, "_Q4", "_Landscape05.tif") ,paste0("Q4/", version_LS_trans, "_Q4", "_Landscape05.tif"))))
```

####USE FOR PL_GAP 
```{r, eval=FALSE}
LS_trans <-  list(
  'NL01' = list(
    'xx01' = c("nlcd01_anC.tif", "nlcd01_anC.tif")), 
  'NL11' = list(
    '0111' = c("nlcd11_anC.tif", "nlcd11_anC.tif")), 
  'RT05'= list(
    'xxRT'= c(paste0(version_LS_trans,"_RT", "_Landscape05.tif") ,paste0(version_LS_trans, "_RT", "_Landscape05.tif"))), 
  'Q105'= list(
    'xxQ1'= c(paste0(version_LS_trans, "_Q1", "_Landscape05.tif") ,paste0( version_LS_trans, "_Q1", "_Landscape05.tif"))),
  'Q205'= list(
    'xxQ2'= c(paste0(version_LS_trans, "_Q2",  "_Landscape05.tif") ,paste0( version_LS_trans, "_Q2", "_Landscape05.tif"))),
  'Q305'= list(
    'xxQ3'= c(paste0(version_LS_trans, "_Q3", "_Landscape05.tif") ,paste0(version_LS_trans, "_Q3", "_Landscape05.tif"))),
  'Q405'= list(
    'xxQ4'= c(paste0(version_LS_trans, "_Q4", "_Landscape05.tif") ,paste0(version_LS_trans, "_Q4", "_Landscape05.tif"))))

```

###Create Forest Only Raster 
```{r, eval=FALSE}

old <- Sys.time() # TIMING SCRIPT

for(scenario in names(LS_trans)){ # Makes code flexible for use with more than 2 landscapes. 
  print(scenario)
  for(in_to_fin in names(LS_trans[[scenario]])){
    print(in_to_fin)
    print(LS_trans[[scenario]][[in_to_fin]][2])
    
    LS_raster <- raster(paste0(RasterLoc, LS_trans[[scenario]][[in_to_fin]][2]))
    LS_raster[LS_raster > 8]<-NA #remove weird noData values like -128, 255...
    
    nlcd_vals <- getValues(LS_raster) 
    LS_5_vals <- ifelse(nlcd_vals == 5| is.na(nlcd_vals), nlcd_vals, 0)
    LS_5 <- setValues(LS_raster, LS_5_vals)
    LS_5[LS_5 <= 0]<-NA
    ```
TURN ON TO MASK TO STUDY AREA 

```{r, eval=FALSE}
LS_5_StudyArea <- raster::mask(LS_5, cnty_saMASK) #use when you want forest stats for the entire county. OR need a raster that is just forest for the entire county 
```

TURN ON TO MASK TO COUNTIES
```{r, eval=FALSE}
  for(i in 1:length(county_saMaskList)){
      county_saMask<-raster(county_saMaskList[[i]][1])
     LS_5_StudyArea<-raster::mask(LS_5,county_saMask)
    ```
    
TURN ON TO MASK TO REGION 
```{r, eval=FALSE}
    for(region in 1:length(region_saMaskList)){
    region_saMask<-raster(region_saMaskList[[region]][1])
    LS_5_StudyArea<-raster::mask(LS_5,region_saMask)
```

WRITE FILE FOR COUNTIES 
```{r, eval=FALSE}
writeRaster(LS_5_StudyArea, filename=paste0(Output_Folder,names(county_saMaskList[i]), scenario,in_to_fin, "_Forest_StudyArea.tif"), format="GTiff", overwrite=TRUE)
```

WRITE FILE FOR STUDY AREA 
```{r, eval=FALSE}
writeRaster(LS_5, filename=paste0(Output_Folder, scenario,in_to_fin, "_Forest_FullArea.tif"), format="GTiff", overwrite=TRUE)
```

Note: For future runs, can start here by reading the above to file

###RUN PATCH STATS 
```{r, eval=FALSE}
library(igraph)
    
    LS_5_clump <- clump(LS_5_StudyArea, directions = 8, gap=FALSE) # detect clumps (patches) and gives unique ID for each of them. Uses the 8-neighbor rule. 
    LS_5_pstat <- PatchStat(LS_5_clump, cellsize = 30) # calculate patch statistics. Statistics based on each patch. 
    
    # ----------------------------------------------
    # CREATE TABLE
    # ----------------------------------------------
    u_patch <- unique(LS_5_clump) #turns patchIDs into numeric 

#---------------------------------------------------------------#
  #OPTION -Probably won't use and will have to adjust the script if needed. Or look at older versions. 
    
    #USE FOR STUDY AREA
    #studyarea_vals <- getValues(regions_StudyArea) 
    #u_vals <- sort(unique(studyarea_vals)[-1]) # Value for each county
 #------------------------------------------------------------------#
  #OPTION
    #USE FOR INDIVIDUAL COUNTIES 
    county_vals<-getValues(county_saMask)
   u_vals<-sort(unique(county_vals)[-1])
  #---------------------------------------------------------------#  
   #OPTION 
      #USE FOR REGIONS 
      #region_vals<-getValues(region_saMask)
      #u_vals<-sort(unique(region_vals)[-1])
   
   
    ### Load dplyr each time bc remove it below. #THIS MAy NEED TO BE CHANGED to COUNTY MASK 
    library(dplyr)
```

RUN FOR REGION 

```{r, eval=FALSE}
   ras_patch <- list()
   n_p <- 1
   for(j in 1:length(u_vals)){
    print(paste0(names(region_saMask),":",u_vals[j]))
       categ_val <- ifelse(region_vals== u_vals[j]|is.na(region_vals),region_vals,NA) 
     categ_p <- setValues(region_saMask, categ_val)
     ras_patch[[n_p]] <- as.data.frame(zonal(categ_p, LS_5_clump, fun='count', na.rm=TRUE))
     ras_patch[[n_p]]$area.ha<-ras_patch[[n_p]]$count*900/10000#Makes sure resolution is right here. 30*30=900, 360*360=129600
     ras_patch[[n_p]]$Raster <- paste0(names(region_saMask))
     ras_patch[[n_p]]$Region <- paste0(u_vals[j])
     n_p <- n_p +1
   
   
   ras_patches<- bind_rows(ras_patch)
```

RUN FOR COUNTY 
```{r, eval=FALSE}
ras_patch <- list()
   n_p <- 1
   for(j in 1:length(u_vals)){
     print(paste0(names(county_saMask),":",u_vals[j]))
     categ_val <- ifelse(county_vals== u_vals[j]|is.na(county_vals),county_vals,NA) 
     categ_p <- setValues(county_saMask, categ_val)
     ras_patch[[n_p]] <- as.data.frame(zonal(categ_p, LS_5_clump, fun='count', na.rm=TRUE))
     ras_patch[[n_p]]$area.ha<-ras_patch[[n_p]]$count*900/10000#Makes sure resolution is right here. 30*30=900, 360*360=129600
     ras_patch[[n_p]]$Raster <- paste0(names(county_saMask))
     ras_patch[[n_p]]$county <- paste0(u_vals[j])
     n_p <- n_p +1
     
     
     ras_patches<- bind_rows(ras_patch)
```

```{r, eval=FALSE}
 write.table(LS_5_pstat, file = paste0(Output_Folder, names(county_saMaskList[i]), scenario, in_to_fin, "_Forest_Pstats.txt"), row.names=FALSE, sep=",")
    
    ### !! Remove dplyr in order to run clump in next round
    detach(name="package:dplyr", unload=TRUE)
    
    
    # ----------------------------------------------
    # RECLASSIFY 
    # ----------------------------------------------
   recl <- ras_patches[,c(1,5)]
    
    LS_5_maj_region <- reclassify(LS_5_clump, recl)		#using the patchID and associated counties from region_maj, it assigns those IDs to the original clump (patches) raster. This is then used to run classstats  
    
    # WRITE TO FILE
    #writeRaster(LS_5_maj_region, filename=paste0(Output_Folder, names(county_saMaskList[i]), scenario, in_to_fin, "_Forest_majregion.tif"), format='GTiff', overwrite=TRUE)
    
    LS_5_cstat <- ClassStat(LS_5_maj_region)
    
    # WRITE TO FILE **!! CHANGE FILE NAME EACH TIME !!**
    write.table(LS_5_cstat, file = paste0(Output_Folder,names(county_saMaskList[i]), scenario, in_to_fin, "_Forest_Cstats.txt"), row.names=FALSE, sep=",")
    
    }
  }
}
}
new<-Sys.time()-old
print(new)
```

##MERGE TABLES 

###REGION CSTAT TABLES 
```{r, eval=FALSE}
version_table<-"U:/CLI/Dinamica_Runs/StudyArea_V201/SA_V2016/BasicDataAnalyses/Forest_Stats/Region/"

Folder<-list.files(paste0(version_table, "NL11"), pattern="110111_Forest_Cstats.txt", full.names = TRUE) #Read in NCLD files 
NL<-lapply(Folder,function(i){
  read.csv(i)
})

NL[[1]]$Region<-"1"
NL[[2]]$Region<-"2"
NL[[3]]$Region<-"3"
NL[[4]]$Region<-"4"
NL[[5]]$Region<-"5"
NL[[6]]$Region<-"6"
NL[[7]]$Region<-"7"
NL[[8]]$Region<-"8"

CombinedNL<-do.call(rbind.data.frame,NL)
CombinedNL$Scenario<-"NL11"

Folder<-list.files(paste0(version_table, "Q1"), pattern="Cstats.txt", full.names = TRUE) 
Q1<-lapply(Folder,function(i){
  read.csv(i)
})

Q1[[1]]$Region<-"1"
Q1[[2]]$Region<-"2"
Q1[[3]]$Region<-"3"
Q1[[4]]$Region<-"4"
Q1[[5]]$Region<-"5"
Q1[[6]]$Region<-"6"
Q1[[7]]$Region<-"7"
Q1[[8]]$Region<-"8"

CombinedQ1<-do.call(rbind.data.frame,Q1)
CombinedQ1$Scenario<-"Q1"

Folder<-list.files(paste0(version_table, "Q2"), pattern="Cstats.txt", full.names = TRUE) #Read in NCLD files 
Q2<-lapply(Folder,function(i){
  read.csv(i)
})

Q2[[1]]$Region<-"1"
Q2[[2]]$Region<-"2"
Q2[[3]]$Region<-"3"
Q2[[4]]$Region<-"4"
Q2[[5]]$Region<-"5"
Q2[[6]]$Region<-"6"
Q2[[7]]$Region<-"7"
Q2[[8]]$Region<-"8"

CombinedQ2<-do.call(rbind.data.frame,Q2)
CombinedQ2$Scenario<-"Q2"

Folder<-list.files(paste0(version_table, "Q3"), pattern="Cstats.txt", full.names = TRUE) #Read in NCLD files 
Q3<-lapply(Folder,function(i){
  read.csv(i)
})   

Q3[[1]]$Region<-"1"
Q3[[2]]$Region<-"2"
Q3[[3]]$Region<-"3"
Q3[[4]]$Region<-"4"
Q3[[5]]$Region<-"5"
Q3[[6]]$Region<-"6"
Q3[[7]]$Region<-"7"
Q3[[8]]$Region<-"8"

CombinedQ3<-do.call(rbind.data.frame,Q3)
CombinedQ3$Scenario<-"Q3"

Folder<-list.files(paste0(version_table, "Q4"), pattern="Cstats.txt", full.names = TRUE) #Read in NCLD files 
Q4<-lapply(Folder,function(i){
  read.csv(i)
})

Q4[[1]]$Region<-"1"
Q4[[2]]$Region<-"2"
Q4[[3]]$Region<-"3"
Q4[[4]]$Region<-"4"
Q4[[5]]$Region<-"5"
Q4[[6]]$Region<-"6"
Q4[[7]]$Region<-"7"
Q4[[8]]$Region<-"8"


CombinedQ4<-do.call(rbind.data.frame,Q4)
CombinedQ4$Scenario<-"Q4"

Folder<-list.files(paste0(version_table, "RT"), pattern="RT05xxRT_Forest_Cstats.txt", full.names = TRUE) #Read in NCLD files 
RT<-lapply(Folder,function(i){
  read.csv(i)
})

RT[[1]]$Region<-"1"
RT[[2]]$Region<-"2"
RT[[3]]$Region<-"3"
RT[[4]]$Region<-"4"
RT[[5]]$Region<-"5"
RT[[6]]$Region<-"6"
RT[[7]]$Region<-"7"
RT[[8]]$Region<-"8"


CombinedRT<-do.call(rbind.data.frame,RT)
CombinedRT$Scenario<-"RT"


Allscenarios<-rbind(CombinedNL, CombinedRT, CombinedQ1, CombinedQ2, CombinedQ3, CombinedQ4)

write.csv(Allscenarios,"U:/CLI/Dinamica_Runs/StudyArea_V201/SA_V2016/BasicDataAnalyses/Forest_Stats/Region/v2016_Fragstats_region.csv")
```

###COUNTY CSTAT TABLES 
```{r, eval=FALSE}
version_table<-"U:/CLI/Dinamica_Runs/StudyArea_V201/SA_V2016/BasicDataAnalyses/Forest_Stats/PL_Gap/County/"






Folder<-list.files(paste0(version_table, "NL"), pattern="110111_Forest_Cstats.txt", full.names = TRUE) #Read in NCLD files 
NL<-lapply(Folder,function(i){
  read.csv(i)
})

NL[[1]]$county<-"Albemarle"
NL[[2]]$county<-"Augusta"
NL[[3]]$county<-"Clarke"
NL[[4]]$county<-"Culpeper"
NL[[5]]$county<-"Fauquier"
NL[[6]]$county<-"Frederick"
NL[[7]]$county<-"Greene"
NL[[8]]$county<-"Loundon"
NL[[9]]$county<-"Madison"
NL[[10]]$county<-"Orange"
NL[[11]]$county<-"Page"
NL[[12]]$county<-"Rappahannock"
NL[[13]]$county<-"Rockingham"
NL[[14]]$county<-"Shenandoah"
NL[[15]]$county<-"Warren"



CombinedNL<-do.call(rbind.data.frame,NL)
CombinedNL$Scenario<-"NL11"


Folder<-list.files(paste0(version_table, "Q1"), pattern="Cstats.txt", full.names = TRUE) 
Q1<-lapply(Folder,function(i){
  read.csv(i)
})

Q1[[1]]$county<-"Albemarle"
Q1[[2]]$county<-"Augusta"
Q1[[3]]$county<-"Clarke"
Q1[[4]]$county<-"Culpeper"
Q1[[5]]$county<-"Fauquier"
Q1[[6]]$county<-"Frederick"
Q1[[7]]$county<-"Greene"
Q1[[8]]$county<-"Loundon"
Q1[[9]]$county<-"Madison"
Q1[[10]]$county<-"Orange"
Q1[[11]]$county<-"Page"
Q1[[12]]$county<-"Rappahannock"
Q1[[13]]$county<-"Rockingham"
Q1[[14]]$county<-"Shenandoah"
Q1[[15]]$county<-"Warren"



CombinedQ1<-do.call(rbind.data.frame,Q1)
CombinedQ1$Scenario<-"Q1"

Folder<-list.files(paste0(version_table, "Q2"), pattern="Cstats.txt", full.names = TRUE) #Read in NCLD files 
Q2<-lapply(Folder,function(i){
  read.csv(i)
})

Q2[[1]]$county<-"Albemarle"
Q2[[2]]$county<-"Augusta"
Q2[[3]]$county<-"Clarke"
Q2[[4]]$county<-"Culpeper"
Q2[[5]]$county<-"Fauquier"
Q2[[6]]$county<-"Frederick"
Q2[[7]]$county<-"Greene"
Q2[[8]]$county<-"Loundon"
Q2[[9]]$county<-"Madison"
Q2[[10]]$county<-"Orange"
Q2[[11]]$county<-"Page"
Q2[[12]]$county<-"Rappahannock"
Q2[[13]]$county<-"Rockingham"
Q2[[14]]$county<-"Shenandoah"
Q2[[15]]$county<-"Warren"



CombinedQ2<-do.call(rbind.data.frame,Q2)
CombinedQ2$Scenario<-"Q2"

Folder<-list.files(paste0(version_table, "Q3"), pattern="Cstats.txt", full.names = TRUE) #Read in NCLD files 
Q3<-lapply(Folder,function(i){
  read.csv(i)
})

Q3[[1]]$county<-"Albemarle"
Q3[[2]]$county<-"Augusta"
Q3[[3]]$county<-"Clarke"
Q3[[4]]$county<-"Culpeper"
Q3[[5]]$county<-"Fauquier"
Q3[[6]]$county<-"Frederick"
Q3[[7]]$county<-"Greene"
Q3[[8]]$county<-"Loundon"
Q3[[9]]$county<-"Madison"
Q3[[10]]$county<-"Orange"
Q3[[11]]$county<-"Page"
Q3[[12]]$county<-"Rappahannock"
Q3[[13]]$county<-"Rockingham"
Q3[[14]]$county<-"Shenandoah"
Q3[[15]]$county<-"Warren"



CombinedQ3<-do.call(rbind.data.frame,Q3)
CombinedQ3$Scenario<-"Q3"

Folder<-list.files(paste0(version_table, "Q4"), pattern="Cstats.txt", full.names = TRUE) #Read in NCLD files 
Q4<-lapply(Folder,function(i){
  read.csv(i)
})

Q4[[1]]$county<-"Albemarle"
Q4[[2]]$county<-"Augusta"
Q4[[3]]$county<-"Clarke"
Q4[[4]]$county<-"Culpeper"
Q4[[5]]$county<-"Fauquier"
Q4[[6]]$county<-"Frederick"
Q4[[7]]$county<-"Greene"
Q4[[8]]$county<-"Loundon"
Q4[[9]]$county<-"Madison"
Q4[[10]]$county<-"Orange"
Q4[[11]]$county<-"Page"
Q4[[12]]$county<-"Rappahannock"
Q4[[13]]$county<-"Rockingham"
Q4[[14]]$county<-"Shenandoah"
Q4[[15]]$county<-"Warren"



CombinedQ4<-do.call(rbind.data.frame,Q4)
CombinedQ4$Scenario<-"Q4"

Folder<-list.files(paste0(version_table, "RT"), pattern="RT05xxRT_Forest_Cstats.txt", full.names = TRUE) #Read in NCLD files 
RT<-lapply(Folder,function(i){
  read.csv(i)
})

RT[[1]]$county<-"Albemarle"
RT[[2]]$county<-"Augusta"
RT[[3]]$county<-"Clarke"
RT[[4]]$county<-"Culpeper"
RT[[5]]$county<-"Fauquier"
RT[[6]]$county<-"Frederick"
RT[[7]]$county<-"Greene"
RT[[8]]$county<-"Loundon"
RT[[9]]$county<-"Madison"
RT[[10]]$county<-"Orange"
RT[[11]]$county<-"Page"
RT[[12]]$county<-"Rappahannock"
RT[[13]]$county<-"Rockingham"
RT[[14]]$county<-"Shenandoah"
RT[[15]]$county<-"Warren"



CombinedRT<-do.call(rbind.data.frame,RT)
CombinedRT$Scenario<-"RT"


Allscenarios<-rbind(CombinedNL, CombinedRT, CombinedQ1, CombinedQ2, CombinedQ3, CombinedQ4)

write.csv(Allscenarios, "U:/CLI/Dinamica_Runs/StudyArea_V201/SA_V2016/BasicDataAnalyses/Forest_Stats/PL_Gap/County/V2016_Fragstats_PL_Ctny.csv", row.names = FALSE)
```

###MERGE CORE AREA TABLES (generated in arcMAP)
```{r, eval=FALSE}
version_table<-"U:/CLI/Dinamica_Runs/StudyArea_V201/SA_V2016/BasicDataAnalyses/Forest_Stats/PL_Gap/CoreArea/FocalStatistics_Core/"

Folder<-list.files(paste0(version_table, "Tables/"), pattern="rgn.csv", full.names = TRUE) #chagne pattern for ctny and rgn 
PL_Core<-lapply(Folder,function(i){
  read.csv(i)
})

PL_Core[[1]]$scenario<-"nl01"
PL_Core[[2]]$scenario<-"nl11"
PL_Core[[3]]$scenario<-"Q1"
PL_Core[[4]]$scenario<-"Q2"
PL_Core[[5]]$scenario<-"Q3"
PL_Core[[6]]$scenario<-"Q4"
PL_Core[[7]]$scenario<-"RT"

CoreAll<-do.call(rbind.data.frame, PL_Core)
CoreAll$Rowid_<-NULL

write.csv(CoreAll, "U:/CLI/Dinamica_Runs/StudyArea_V201/SA_V2016/BasicDataAnalyses/Forest_Stats/PL_Gap/CoreArea/FocalStatistics_Core/Tables/v2016_AllScenarios_CoreArea_pl_rgn.csv", row.names = FALSE)
```
