---
title: "ForestPatches_Graphs_8-2-2018"
author: "Sarah Halperin"
date: "August 10, 2018"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

##INTRODUCTION 

Generate ggplots for tables created in ForestPatches_nlcdOnly_8-2-2018 or the RMD file RMD_ForestPatches_8-2-2018

###PACKAGES
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(ggplot2)
library(raster)
library(dplyr)
library(Hmisc)
library(reshape)
```

##FragStats Graphs 


###Fragstats by study area

```{r}
StudyAreaStats<-read.csv("U:/CLI/Dinamica_Runs/StudyArea_V201/SA_V2016/BasicDataAnalyses/OutputVisuals/Fragstats/StudyArea/v2016_fragstats_studyarea.csv")
```

####mean_patch
```{r, fig.height=15, fig.width=15}
ggplot(StudyAreaStats, aes(x=Scenario, y=mean.patch.areakm, fill=Scenario))+
  geom_bar(stat="identity", position="dodge")+
  scale_fill_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  xlab("County")+
  scale_y_continuous(name =expression('Mean Patch Area km'^2))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

####n_patches
```{r, fig.width=15, fig.height=15}
ggplot(StudyAreaStats, aes(x=Scenario, y=n.patches, fill=Scenario))+
  geom_bar(stat="identity", position="dodge")+
  scale_fill_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  xlab("County")+
  scale_y_continuous(name = "Number of Patches")+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

####prop.landscape 
```{r, fig.height=15, fig.width=15}

StudyAreaStats$prop.landscapePC<-StudyAreaStats$prop.landscapePC*100

ggplot(StudyAreaStats, aes(x=Scenario, y=prop.landscapePC, fill=Scenario))+
  geom_bar(stat="identity", position="dodge")+
    scale_fill_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  scale_y_continuous(name = "Proportion of the Landscape %", limits =c(0,60), breaks = c(10,20,30,40,50))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

####CoreArea 
```{r, fig.height=15, fig.width=15}
ggplot(StudyAreaStats, aes(x=Scenario, y=CoreAreakm, fill=Scenario))+
  geom_bar(stat="identity", position="dodge")+
    scale_fill_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  scale_y_continuous(name =expression('Area km'^2))+
  coord_cartesian(ylim=c(200,750))+
  xlab("County")+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

###Fragstats by county 


Example for Frederick and Fauquier 
```{r, fig.width=15, fig.height=15,eval=FALSE, include=FALSE}
Cstats<-read.csv("U:/CLI/Dinamica_Runs/StudyArea_V201/SA_V2016/BasicDataAnalyses/Forest_Stats/County/V2016_Fragstats_Ctny.csv")
Cstats$mean.patch.areakm<-Cstats$mean.patch.area*(900/1000000) #convert from pixels 

CstatsFauq<-subset(Cstats, Cstats$county == "Fauquier")
CstatsFred<-subset(Cstats, Cstats$county == "Frederick")

CstatsFF<-rbind(CstatsFauq, CstatsFred)
CstatsFF<-subset(CstatsFF, CstatsFF$Scenario %in%  c("RT", "Q1", "Q2", "Q3", "Q4"))
```

####mean_patch 
```{r, fig.width=15, fig.height=15, eval=FALSE, include=FALSE}
CstatsFF$county<-factor(CstatsFF$county, levels=c("Frederick", "Fauquier"))

#name if you want to save the file 
ggplot(CstatsFF, aes(x=county, y=mean.patch.areakm, fill=Scenario))+
  geom_bar(stat="identity", position="dodge")+
  scale_x_discrete(breaks= c("Frederick", "Fauquier"), labels=c("Frederick", "Fauquier"))+
  scale_fill_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  xlab("County")+
  scale_y_continuous(name =expression('Mean Patch Area km'^2))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

```{r, eval=FALSE, include=FALSE}
setwd("U:/CLI/Presentations/ESA-08-XX-2018")
png("v2016_FredFauq_Forestmeanpatch.png", width=480, height=480, units="px", res=300) #can't put units and resolution
FFMP
dev.off()


ggsave(file="v2016_FredFauq_Forestmeanpatch.png", dpi=300,width=15, height=15)


```
####n_patches
```{r, fig.width=15, fig.height=15, eval=FALSE, include=FALSE}
ggplot(CstatsFF, aes(x=county, y=n.patches, fill=Scenario))+
  geom_bar(stat="identity", position="dodge")+
  scale_x_discrete(breaks= c("Frederick", "Fauquier"), labels=c("Frederick", "Fauquier"))+
  scale_fill_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  xlab("County")+
  scale_y_continuous(name = "Number of Patches")+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

```{r, eval=FALSE, include=FALSE}
setwd("U:/CLI/Presentations/ESA-08-XX-2018")
png("v2016_FredFauq_n_patches.png", width=480, height=480, units="px", res=300) #can't put units and resolution
v2016_FredFauq_n_patches
dev.off()


ggsave(file="v2016_FredFauq_n_patches.png", dpi=300,width=15, height=15)
```
####prop_landscape

Need to find proportion because when we calculated the fragstats for each county it no longer calculated proportion correctly 
```{r, eval=FALSE, include=FALSE}
Raster_SA<-raster("V:/IaraSpatialLayers/PreparedRasters/StudyAreaBndy/regions_StudyArea.tif")  

sa_ctyGEOID<-read.csv("V:/IaraSpatialLayers/Dinamica_Runs/StudyArea_V201/SAcntyOnly.csv")#SCBI V: #Geological ID for the county. 

colnames(sa_ctyGEOID)<-c("Din_cty", "GEOID","NAME")
sa_ctyGEOID$NAME<-NULL


Raster_values<-getValues(Raster_SA)
Raster_final<- summary(factor(Raster_values), maxsum = length(unique(Raster_values)))

sa_ctyGEOID$Areapx<-Raster_final[1:20]
sa_ctyGEOID$Areakm<-sa_ctyGEOID$Areapx*(900/1000000)
colnames(sa_ctyGEOID)<-c("class","GEOID", "Areapx", "Areakm")
TotalArea<-sum(sa_ctyGEOID$Areakm) #17888.25

#C_statsCombined<-merge(C_statsCombined,sa_ctyGEOID, by ="class")

sa_ctyGEOIDFF<-subset(sa_ctyGEOID, sa_ctyGEOID$class %in% c(3,10))
sa_ctyGEOIDFF$county<-c("Frederick", "Fauquier")
CstatsFFprop<-merge(sa_ctyGEOIDFF,CstatsFF, by="county")

CstatsFFprop$total.areakm<-CstatsFFprop$total.area*(900/1000000)

Area<-read.csv("U:/CLI/Presentations/ESA-08-XX-2018/v2016_5_CoreAreaTotalArea.csv")

CstatsFFprop$total.area<-Area$TotalAreakm #uses area from zonal histograms. Doesn't really make a difference 

CstatsFFpropF3<-subset(CstatsFFprop, CstatsFFprop == "Frederick")


CstatsFFpropF3$prop.landscape<-(CstatsFFpropF3$total.areakm/CstatsFFpropF3$Areakm)

CstatsFFpropF10<-subset(CstatsFFprop, CstatsFFprop == "Fauquier")
CstatsFFpropF10$prop.landscape<-(CstatsFFpropF10$total.areakm/CstatsFFpropF10$Areakm)

C_statsFFpropcombined<-rbind(CstatsFFpropF3,CstatsFFpropF10)

C_statsFFpropcombined$prop.landscapePC<-C_statsFFpropcombined$prop.landscape*100

```

```{r, fig.width=15, fig.height=15, eval=FALSE}

C_statsFFpropcombined$county<-factor(C_statsFFpropcombined$county, levels=c("Frederick", "Fauquier"))

ggplot(C_statsFFpropcombined, aes(x=county, y=prop.landscapePC, fill=Scenario))+
  geom_bar(stat="identity", position="dodge")+
  scale_x_discrete(name="County", breaks= c("Frederick", "Fauquier"))+
  scale_fill_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  scale_y_continuous(name = "Proportion of the Landscape %", limits =c(0,60), breaks = c(10,20,30,40,50))+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```
```{r, eval=FALSE}
setwd("U:/CLI/Presentations/ESA-08-XX-2018")
png("v2016_FredFauq_proplandscape.png", width=480, height=480, units="px", res=300) #can't put units and resolution
FFprop
dev.off()


ggsave(file="v2016_FredFauq_proplandscape.png", dpi=300,width=15, height=15)

```

####Compare total and core area 
Used for ESA and can update if needed, will have to remake the csv
```{r, fig.width=15, fig.height=15, eval=FALSE, include=FALSE }
Area<-read.csv("U:/CLI/Presentations/ESA-08-XX-2018/v2016_5_CoreAreaTotalArea.csv")


MeltArea<-melt(Area, id=c("county", "Scenario"))

MeltAreaFred<-subset(MeltArea, MeltArea$county == "Frederick")
MeltAreaFauq<-subset(MeltArea, MeltArea$county == "Fauquier")

ggplot(MeltArea, aes(x=variable, y=value, fill=Scenario))+
  geom_bar(stat="identity", position="dodge")+
  scale_fill_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  scale_x_discrete(labels=c("Total Core Area", "Total Area"))+
  scale_y_continuous(name =expression('Area km'^2), limits = c(0,600))+
  xlab("Forest Metric")+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
    
```

```{r, eval=FALSE, include=FALSE}
setwd("U:/CLI/Presentations/ESA-08-XX-2018")
png("v2016_Fred_CoreTotalArea.png", width=480, height=480, units="px", res=300) #can't put units and resolution
FredCoreArea
dev.off()

ggsave(file="v2016_Fred_CoreTotalArea.png", dpi=300, width=15, height=15)
```

####Compare core area and seperately compare total area 


```{r, fig.width=15, fig.height=15, eval=FALSE, include=FALSE}
Area$county<-factor(Area$county, levels=c("Frederick", "Fauquier"))

ggplot(Area, aes(x=county, y=TotalAreakm, fill=Scenario))+
  geom_bar(stat="identity", position="dodge")+
  scale_fill_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  scale_y_continuous(name =expression('Area km'^2))+
  coord_cartesian(ylim=c(200,750))+
  xlab("County")+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())


ggplot(Area, aes(x=county, y=CoreAreakm, fill=Scenario))+
  geom_bar(stat="identity", position="dodge")+
  scale_fill_manual(values=c("#FF0404", "#FF9933","#106A0F", "#0070C1","#330066"))+
  scale_y_continuous(name =expression('Area km'^2))+
  coord_cartesian(ylim=c(200,750))+
  xlab("County")+
  theme_bw()+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.title.x = element_text(margin=margin(t=20, r=0, b=0, l =0)))+
  theme(axis.text=element_text(size=40, colour="black"),
        axis.title.x=element_text(size=40), axis.title.y =element_text(size=40, face="bold"), legend.text=element_text(size=20), legend.title=element_blank(), legend.key.height= unit(1,"in"))+
  theme(plot.margin=unit(c(1,1,1,1), "in"))+
  theme(axis.line = element_line(size=1.5, colour="grey69"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

```{r, eval=FALSE, include=FALSE}
setwd("U:/CLI/Presentations/ESA-08-XX-2018")
png("v2016_5_FredFauq_TotalArea.png", width=480, height=480, units="px", res=300) #can't put units and resolution
FFTotalArea
dev.off()

ggsave(file="v2016_5_FredFauq_TotalArea.png", dpi=300, width=15, height=15)
```
